\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{r|X}
\toprule
{\bf Group Name} & {\bf Description} \\ 
\midrule

ohpc-arm1-io-libs & Collection of IO library builds for use with the Arm Compiler for Linux toolchain. \\ 
\hline
ohpc-arm1-mpich-parallel-libs & Collection of parallel library builds for use with the Arm Compiler for Linux and the MPICH runtime. \\ 
\hline
ohpc-arm1-openmpi4-parallel-libs & Collection of parallel library builds for use with the Arm Compiler for Linux and the openmpi4 runtime. \\ 
\hline
ohpc-arm1-perf-tools & Collection of performance tool builds for use with the Arm Compiler for Linux toolchain. \\ 
\hline
ohpc-arm1-python3-libs & Collection of python3 related library builds for use with the Arm Compiler for Linux toolchain. \\ 
\hline
ohpc-arm1-serial-libs & Collection of serial library builds for use with the Arm Compiler for Linux toolchain. \\ 
\hline
ohpc-autotools & Collection of GNU autotools packages. \\ 
\hline
ohpc-base & Collection of base packages. \\ 
\hline
ohpc-base-compute & Collection of compute node base packages. \\ 
\hline
ohpc-gnu12-geopm & Global Extensible Open Power Manager for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu12-io-libs & Collection of IO library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu12-mpich-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu12-mpich-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu12-mpich-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu12-openmpi4-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu12-openmpi4-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu12-openmpi4-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu12-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu12-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu12-python-libs & Collection of python related library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu12-python3-libs & Collection of python3 related library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu12-runtimes & Collection of runtimes for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu12-serial-libs & Collection of serial library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-geopm & Global Extensible Open Power Manager for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-io-libs & Collection of IO library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-mpich-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu9-mpich-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu9-mpich-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu9-openmpi4-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
\bottomrule
\end{tabularx}
