\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for dimemas
dimemas-gnu12-impi-ohpc &
\multirow{12}{*}{5.4.2} &
\multirow{12}{\linewidth}{Dimemas tool. \newline {\color{logoblue} \url{https://tools.bsc.es}}}\\
dimemas-gnu12-mpich-ohpc &
& \\
dimemas-gnu12-mvapich2-ohpc &
& \\
dimemas-gnu12-openmpi4-ohpc &
& \\
dimemas-gnu9-impi-ohpc &
& \\
dimemas-gnu9-mpich-ohpc &
& \\
dimemas-gnu9-mvapich2-ohpc &
& \\
dimemas-gnu9-openmpi4-ohpc &
& \\
dimemas-intel-impi-ohpc &
& \\
dimemas-intel-mpich-ohpc &
& \\
dimemas-intel-mvapich2-ohpc &
& \\
dimemas-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for dimemas

% <-- begin entry for extrae
extrae-gnu9-impi-ohpc &
\multirow{4}{*}{3.7.0} &
\multirow{12}{\linewidth}{Extrae tool. \newline {\color{logoblue} \url{https://tools.bsc.es}}}\\
extrae-gnu9-mpich-ohpc &
& \\
extrae-gnu9-mvapich2-ohpc &
& \\
extrae-gnu9-openmpi4-ohpc &
& \\
\cline{1-2} extrae-gnu12-impi-ohpc &\multirow{8}{*}{3.8.3}
& \\
extrae-gnu12-mpich-ohpc &
& \\
extrae-gnu12-mvapich2-ohpc &
& \\
extrae-gnu12-openmpi4-ohpc &
& \\
extrae-intel-impi-ohpc &
& \\
extrae-intel-mpich-ohpc &
& \\
extrae-intel-mvapich2-ohpc &
& \\
extrae-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for extrae

% <-- begin entry for geopm
geopm-gnu12-impi-ohpc &
\multirow{12}{*}{1.1.0} &
\multirow{12}{\linewidth}{Global Extensible Open Power Manager. \newline {\color{logoblue} \url{https://geopm.github.io}}}\\
geopm-gnu12-mpich-ohpc &
& \\
geopm-gnu12-mvapich2-ohpc &
& \\
geopm-gnu12-openmpi4-ohpc &
& \\
geopm-gnu9-impi-ohpc &
& \\
geopm-gnu9-mpich-ohpc &
& \\
geopm-gnu9-mvapich2-ohpc &
& \\
geopm-gnu9-openmpi4-ohpc &
& \\
geopm-intel-impi-ohpc &
& \\
geopm-intel-mpich-ohpc &
& \\
geopm-intel-mvapich2-ohpc &
& \\
geopm-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for geopm

% <-- begin entry for imb
imb-gnu9-impi-ohpc &
\multirow{4}{*}{2019.6} &
\multirow{12}{\linewidth}{Intel MPI Benchmarks (IMB). \newline {\color{logoblue} \url{https://software.intel.com/en-us/articles/intel-mpi-benchmarks}}}\\
imb-gnu9-mpich-ohpc &
& \\
imb-gnu9-mvapich2-ohpc &
& \\
imb-gnu9-openmpi4-ohpc &
& \\
\cline{1-2} imb-gnu12-impi-ohpc &\multirow{8}{*}{2021.3}
& \\
imb-gnu12-mpich-ohpc &
& \\
imb-gnu12-mvapich2-ohpc &
& \\
imb-gnu12-openmpi4-ohpc &
& \\
imb-intel-impi-ohpc &
& \\
imb-intel-mpich-ohpc &
& \\
imb-intel-mvapich2-ohpc &
& \\
imb-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for imb

% <-- begin entry for likwid
likwid-gnu9-ohpc &
\multirow{1}{*}{5.0.1} &
\multirow{3}{\linewidth}{Performance tools for the Linux console. \newline {\color{logoblue} \url{https://github.com/RRZE-HPC/likwid}}}\\
\cline{1-2} likwid-gnu12-ohpc &\multirow{2}{*}{5.2.2}
& \\
likwid-intel-ohpc &
& \\
\hline
% <-- end entry for likwid

% <-- begin entry for msr-safe-ohpc
\multirow{2}{*}{msr-safe-ohpc} &
\multirow{2}{*}{1.6.0} &
Allows safer access to model specific registers (MSRs). \newline { \color{logoblue} \url{https://github.com/LLNL/msr-safe}}
\\ \hline
% <-- end entry for msr-safe-ohpc

% <-- begin entry for omb
omb-gnu9-impi-ohpc &
\multirow{4}{*}{5.8} &
\multirow{12}{\linewidth}{OSU Micro-benchmarks. \newline {\color{logoblue} \url{http://mvapich.cse.ohio-state.edu/benchmarks}}}\\
omb-gnu9-mpich-ohpc &
& \\
omb-gnu9-mvapich2-ohpc &
& \\
omb-gnu9-openmpi4-ohpc &
& \\
\cline{1-2} omb-gnu12-impi-ohpc &\multirow{8}{*}{6.1}
& \\
omb-gnu12-mpich-ohpc &
& \\
omb-gnu12-mvapich2-ohpc &
& \\
omb-gnu12-openmpi4-ohpc &
& \\
omb-intel-impi-ohpc &
& \\
omb-intel-mpich-ohpc &
& \\
omb-intel-mvapich2-ohpc &
& \\
omb-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for omb

% <-- begin entry for paraver-ohpc
\multirow{2}{*}{paraver-ohpc} &
\multirow{2}{*}{4.10.4} &
Paraver. \newline { \color{logoblue} \url{https://tools.bsc.es}}
\\ \hline
% <-- end entry for paraver-ohpc

% <-- begin entry for papi57-ohpc
\multirow{2}{*}{papi57-ohpc} &
\multirow{2}{*}{5.7.0} &
Performance Application Programming Interface. \newline { \color{logoblue} \url{http://icl.cs.utk.edu/papi}}
\\ \hline
% <-- end entry for papi57-ohpc

% <-- begin entry for papi-ohpc
\multirow{2}{*}{papi-ohpc} &
\multirow{2}{*}{6.0.0} &
Performance Application Programming Interface. \newline { \color{logoblue} \url{http://icl.cs.utk.edu/papi}}
\\ \hline
% <-- end entry for papi-ohpc

% <-- begin entry for pdtoolkit
pdtoolkit-gnu12-ohpc &
\multirow{3}{*}{3.25.1} &
\multirow{3}{\linewidth}{PDT is a framework for analyzing source code. \newline {\color{logoblue} \url{http://www.cs.uoregon.edu/Research/pdt}}}\\
pdtoolkit-gnu9-ohpc &
& \\
pdtoolkit-intel-ohpc &
& \\
\hline
% <-- end entry for pdtoolkit

% <-- begin entry for scalasca
scalasca-gnu12-impi-ohpc &
\multirow{12}{*}{2.5} &
\multirow{12}{\linewidth}{Toolset for performance analysis of large-scale parallel applications. \newline {\color{logoblue} \url{http://www.scalasca.org}}}\\
scalasca-gnu12-mpich-ohpc &
& \\
scalasca-gnu12-mvapich2-ohpc &
& \\
scalasca-gnu12-openmpi4-ohpc &
& \\
scalasca-gnu9-impi-ohpc &
& \\
scalasca-gnu9-mpich-ohpc &
& \\
scalasca-gnu9-mvapich2-ohpc &
& \\
scalasca-gnu9-openmpi4-ohpc &
& \\
scalasca-intel-impi-ohpc &
& \\
scalasca-intel-mpich-ohpc &
& \\
scalasca-intel-mvapich2-ohpc &
& \\
scalasca-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for scalasca

% <-- begin entry for scorep
scorep-gnu9-impi-ohpc &
\multirow{4}{*}{6.0} &
\multirow{12}{\linewidth}{Scalable Performance Measurement Infrastructure for Parallel Codes. \newline {\color{logoblue} \url{http://www.vi-hps.org/projects/score-p}}}\\
scorep-gnu9-mpich-ohpc &
& \\
scorep-gnu9-mvapich2-ohpc &
& \\
scorep-gnu9-openmpi4-ohpc &
& \\
\cline{1-2} scorep-gnu12-impi-ohpc &\multirow{8}{*}{7.1}
& \\
scorep-gnu12-mpich-ohpc &
& \\
scorep-gnu12-mvapich2-ohpc &
& \\
scorep-gnu12-openmpi4-ohpc &
& \\
scorep-intel-impi-ohpc &
& \\
scorep-intel-mpich-ohpc &
& \\
scorep-intel-mvapich2-ohpc &
& \\
scorep-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for scorep

% <-- begin entry for tau
tau-gnu9-impi-ohpc &
\multirow{4}{*}{2.29} &
\multirow{12}{\linewidth}{Tuning and Analysis Utilities Profiling Package. \newline {\color{logoblue} \url{http://www.cs.uoregon.edu/research/tau/home.php}}}\\
tau-gnu9-mpich-ohpc &
& \\
tau-gnu9-mvapich2-ohpc &
& \\
tau-gnu9-openmpi4-ohpc &
& \\
\cline{1-2} tau-gnu12-impi-ohpc &\multirow{8}{*}{2.31.1}
& \\
tau-gnu12-mpich-ohpc &
& \\
tau-gnu12-mvapich2-ohpc &
& \\
tau-gnu12-openmpi4-ohpc &
& \\
tau-intel-impi-ohpc &
& \\
tau-intel-mpich-ohpc &
& \\
tau-intel-mvapich2-ohpc &
& \\
tau-intel-openmpi4-ohpc &
& \\
\hline
% <-- end entry for tau

\bottomrule
\end{tabularx}
