Global Extensible Open Power Manager (\GEOPM{}) is a framework for exploring
power and energy optimizations targeting high performance computing.  The
library can be extended to support new control algorithms and new
hardware-specific power management features.  The \GEOPM{} package provides
built-in features ranging from static management of power policy for each
individual compute node, to dynamic coordination of power policy and
performance across all of the compute nodes hosting one MPI job on a portion of
a distributed computing system.  The dynamic coordination is implemented as a
hierarchical control system for scalable communication and decentralized
control. The following commands can be used to configure execution of the
\GEOPM{} runtime on the {\em compute} hosts. The packages themselves will be
installed in a later step.

% begin_ohpc_run
% ohpc_validation_newline
% ohpc_command if [[ ${enable_geopm} -eq 1 ]];then
% ohpc_indent 5
\begin{lstlisting}[language=bash,keywords={},upquote=true]
# Disable Intel pstate driver for compute nodes because it interferes with GEOPM's operation.
[sms](*\#*) export kargs="${kargs} intel_pstate=disable"
\end{lstlisting}
% ohpc_indent 0
% ohpc_command fi
% end_ohpc_run

\noindent The \GEOPM{} package uses \OHPC{}'s msr-safe kernel module
to enable users to directly read and write whitelisted Model Specific
Registers (MSRs).  An associated \SLURM{} plugin ensures that MSRs modified
within a user slurm job allocation are reset to their original state
before the compute node is returned to the pool available to other
users of the system.

% begin_ohpc_run
% ohpc_validation_newline
% ohpc_command if [[ ${enable_geopm} -eq 1 ]];then
% ohpc_indent 5
\begin{lstlisting}[language=bash,keywords={},upquote=true]
# Install msr-safe kernel module and SLURM plugin
[sms](*\#*) (*\chrootinstall*) kmod-msr-safe-ohpc
[sms](*\#*) (*\chrootinstall*) msr-safe-slurm-ohpc
\end{lstlisting}
% ohpc_indent 0
% ohpc_command fi
% end_ohpc_run

For documentation on how to use \GEOPM{} please see
the \GEOPM{} man pages which are all linked from the geopm(7) overview
man page available in html here:
\href{http://geopm.github.io/man/geopm.7.html}
{\color{blue}{http://geopm.github.io/man/geopm.7.html}}.
Please see the \GEOPM{} tutorials and for working examples using the
\GEOPM{} runtime here: \href{https://github.com/geopm/geopm/tree/dev/tutorial}
{\color{blue}{https://github.com/geopm/geopm/tree/dev/tutorial}}.
