%\newpage

\vspace*{3.0cm}
\noindent {\Large \color{RoyalBlue} \fontfamily{phv}\selectfont Legal Notice} \\ 

\vspace*{0.5cm}

\noindent Copyright {\small\copyright} 2015, Intel Corporation. All rights reserved. \\
%\noindent {\small\copyright} 2015 Intel Corporation

\noindent Redistribution and use in source and binary forms, with or without
modification, are permitted provided that the following conditions are met:

\begin{itemize*}
\item Redistributions of source code must retain the above copyright notice,
      this list of conditions \\ and the 
      following disclaimer.
\item Redistributions in binary form (PDF, HTML, RTF, shell script, PostScript,
      etc.), must \\ reproduce the above copyright notice, this list of conditions
      and the following disclaimer \\ in the documentation and/or other materials
      provided with the distribution.
\item Neither the name of Intel Corporation nor the names of its contributors
      may be used \\ to endorse or promote products derived from this
      documentation
      without specific prior \\ written permission.
\end{itemize*} 

\vspace*{0.5cm}

{\footnotesize

\noindent THIS DOCUMENTATION IS PROVIDED BY THE COPYRIGHT HOLDERS AND
CONTRIBUTORS ``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT
NOT LIMITED TO, THE
IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE
FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE. \\

\noindent Intel technologies features and benefits depend on system
configuration and may require enabled hardware, software or service
activation. \\

\noindent No computer system can be absolutely secure. Intel does not control
or audit third-party benchmark data or the web sites referenced in this
document. You should visit the referenced web site and confirm whether
referenced data are accurate.  \\

\noindent Learn more at intel.com, or from the OEM or retailer. \\

\noindent The products described may contain design defects or errors known as
errata which may cause the product to deviate from published
specifications. Current characterized errata are available on request. \\

\noindent Intel, the Intel logo, and others are trademarks of Intel Corporation
in the U.S. and/or other countries. \\

\noindent *Other names and brands may be claimed as the property of others. \\



}
