\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for adios
adios-gnu-mpich-ohpc &
\multirow{3}{*}{1.12.0} & 
\multirow{7}{\linewidth}{The Adaptable IO System (ADIOS). \newline {\color{logoblue} \url{http://www.olcf.ornl.gov/center-projects/adios}}} \\ 
adios-gnu-openmpi-ohpc &
& \\ 
adios-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} adios-gnu7-mpich-ohpc &\multirow{4}{*}{1.13.1}
& \\ 
adios-gnu7-openmpi3-ohpc &
& \\ 
adios-gnu8-mpich-ohpc &
& \\ 
adios-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for adios

% <-- begin entry for hdf5
hdf5-gnu-ohpc &
\multirow{1}{*}{1.10.1} & 
\multirow{3}{\linewidth}{A general purpose library and file format for storing scientific data. \newline {\color{logoblue} \url{http://www.hdfgroup.org/HDF5}}} \\ 
\cline{1-2} hdf5-gnu7-ohpc &\multirow{1}{*}{1.10.2}
& \\ 
\cline{1-2} hdf5-gnu8-ohpc &\multirow{1}{*}{1.10.4}
& \\ 
\hline
% <-- end entry for hdf5

% <-- begin entry for netcdf-cxx
netcdf-cxx-gnu-mpich-ohpc &
\multirow{7}{*}{4.3.0} & 
\multirow{7}{\linewidth}{C++ Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}} \\ 
netcdf-cxx-gnu-openmpi-ohpc &
& \\ 
netcdf-cxx-gnu7-mpich-ohpc &
& \\ 
netcdf-cxx-gnu7-openmpi-ohpc &
& \\ 
netcdf-cxx-gnu7-openmpi3-ohpc &
& \\ 
netcdf-cxx-gnu8-mpich-ohpc &
& \\ 
netcdf-cxx-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for netcdf-cxx

% <-- begin entry for netcdf-fortran
netcdf-fortran-gnu-mpich-ohpc &
\multirow{5}{*}{4.4.4} & 
\multirow{7}{\linewidth}{Fortran Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}} \\ 
netcdf-fortran-gnu-openmpi-ohpc &
& \\ 
netcdf-fortran-gnu7-mpich-ohpc &
& \\ 
netcdf-fortran-gnu7-openmpi-ohpc &
& \\ 
netcdf-fortran-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} netcdf-fortran-gnu8-mpich-ohpc &\multirow{2}{*}{4.4.5}
& \\ 
netcdf-fortran-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for netcdf-fortran

% <-- begin entry for netcdf
netcdf-gnu-mpich-ohpc &
\multirow{3}{*}{4.5.0} & 
\multirow{7}{\linewidth}{C Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}} \\ 
netcdf-gnu-openmpi-ohpc &
& \\ 
netcdf-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} netcdf-gnu7-mpich-ohpc &\multirow{3}{*}{4.6.1}
& \\ 
netcdf-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} netcdf-gnu8-mpich-ohpc &\multirow{2}{*}{4.6.2}
& \\ 
netcdf-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for netcdf

% <-- begin entry for phdf5
phdf5-gnu-mpich-ohpc &
\multirow{3}{*}{1.10.1} & 
\multirow{7}{\linewidth}{A general purpose library and file format for storing scientific data. \newline {\color{logoblue} \url{http://www.hdfgroup.org/HDF5}}} \\ 
phdf5-gnu-openmpi-ohpc &
& \\ 
phdf5-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} phdf5-gnu7-mpich-ohpc &\multirow{3}{*}{1.10.2}
& \\ 
phdf5-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} phdf5-gnu8-mpich-ohpc &\multirow{2}{*}{1.10.4}
& \\ 
phdf5-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for phdf5

% <-- begin entry for pnetcdf
pnetcdf-gnu7-openmpi-ohpc &
\multirow{1}{*}{1.8.1} & 
\multirow{5}{\linewidth}{A Parallel NetCDF library (PnetCDF). \newline {\color{logoblue} \url{http://cucis.ece.northwestern.edu/projects/PnetCDF}}} \\ 
\cline{1-2} pnetcdf-gnu7-mpich-ohpc &\multirow{3}{*}{1.9.0}
& \\ 
pnetcdf-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} pnetcdf-gnu8-mpich-ohpc &\multirow{2}{*}{1.11.0}
& \\ 
pnetcdf-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for pnetcdf

% <-- begin entry for sionlib
sionlib-gnu-mpich-ohpc &
\multirow{5}{*}{1.7.1} & 
\multirow{7}{\linewidth}{Scalable I/O Library for Parallel Access to Task-Local Files. \newline {\color{logoblue} \url{http://www.fz-juelich.de/ias/jsc/EN/Expertise/Support/Software/SIONlib/_node.html}}} \\ 
sionlib-gnu-openmpi-ohpc &
& \\ 
sionlib-gnu7-mpich-ohpc &
& \\ 
sionlib-gnu7-openmpi-ohpc &
& \\ 
sionlib-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} sionlib-gnu8-mpich-ohpc &\multirow{2}{*}{1.7.2}
& \\ 
sionlib-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for sionlib

\bottomrule
\end{tabularx}
