\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for dimemas
dimemas-gnu8-mpich-ohpc &
\multirow{2}{*}{5.3.4} & 
\multirow{2}{\linewidth}{Dimemas tool. \newline {\color{logoblue} \url{https://tools.bsc.es}}} \\ 
dimemas-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for dimemas

% <-- begin entry for extrae
extrae-gnu8-mpich-ohpc &
\multirow{2}{*}{3.5.2} & 
\multirow{2}{\linewidth}{Extrae tool. \newline {\color{logoblue} \url{https://tools.bsc.es}}} \\ 
extrae-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for extrae

% <-- begin entry for imb
imb-gnu-mpich-ohpc &
\multirow{7}{*}{2018.1} & 
\multirow{7}{\linewidth}{Intel MPI Benchmarks (IMB). \newline {\color{logoblue} \url{https://software.intel.com/en-us/articles/intel-mpi-benchmarks}}} \\ 
imb-gnu-openmpi-ohpc &
& \\ 
imb-gnu7-mpich-ohpc &
& \\ 
imb-gnu7-openmpi-ohpc &
& \\ 
imb-gnu7-openmpi3-ohpc &
& \\ 
imb-gnu8-mpich-ohpc &
& \\ 
imb-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for imb

% <-- begin entry for mpiP
mpiP-gnu-mpich-ohpc &
\multirow{7}{*}{3.4.1} & 
\multirow{7}{\linewidth}{mpiP: a lightweight profiling library for MPI applications. \newline {\color{logoblue} \url{http://mpip.sourceforge.net}}} \\ 
mpiP-gnu-openmpi-ohpc &
& \\ 
mpiP-gnu7-mpich-ohpc &
& \\ 
mpiP-gnu7-openmpi-ohpc &
& \\ 
mpiP-gnu7-openmpi3-ohpc &
& \\ 
mpiP-gnu8-mpich-ohpc &
& \\ 
mpiP-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for mpiP

% <-- begin entry for paraver-ohpc
\multirow{2}{*}{paraver-ohpc} & 
\multirow{2}{*}{4.7.2} & 
Paraver. \newline { \color{logoblue} \url{https://tools.bsc.es}} 
\\ \hline 
% <-- end entry for paraver-ohpc

% <-- begin entry for papi-ohpc
\multirow{2}{*}{papi-ohpc} & 
\multirow{2}{*}{5.6.0} & 
Performance Application Programming Interface. \newline { \color{logoblue} \url{http://icl.cs.utk.edu/papi}} 
\\ \hline 
% <-- end entry for papi-ohpc

% <-- begin entry for pdtoolkit
pdtoolkit-gnu-ohpc &
\multirow{3}{*}{3.25} & 
\multirow{3}{\linewidth}{PDT is a framework for analyzing source code. \newline {\color{logoblue} \url{http://www.cs.uoregon.edu/Research/pdt}}} \\ 
pdtoolkit-gnu7-ohpc &
& \\ 
pdtoolkit-gnu8-ohpc &
& \\ 
\hline
% <-- end entry for pdtoolkit

% <-- begin entry for scalasca
scalasca-gnu-mpich-ohpc &
\multirow{5}{*}{2.3.1} & 
\multirow{7}{\linewidth}{Toolset for performance analysis of large-scale parallel applications. \newline {\color{logoblue} \url{http://www.scalasca.org}}} \\ 
scalasca-gnu-openmpi-ohpc &
& \\ 
scalasca-gnu7-mpich-ohpc &
& \\ 
scalasca-gnu7-openmpi-ohpc &
& \\ 
scalasca-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} scalasca-gnu8-mpich-ohpc &\multirow{2}{*}{2.4}
& \\ 
scalasca-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for scalasca

% <-- begin entry for scorep
scorep-gnu-mpich-ohpc &
\multirow{3}{*}{3.1} & 
\multirow{7}{\linewidth}{Scalable Performance Measurement Infrastructure for Parallel Codes. \newline {\color{logoblue} \url{http://www.vi-hps.org/projects/score-p}}} \\ 
scorep-gnu-openmpi-ohpc &
& \\ 
scorep-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} scorep-gnu7-mpich-ohpc &\multirow{3}{*}{4.0}
& \\ 
scorep-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} scorep-gnu8-mpich-ohpc &\multirow{2}{*}{4.1}
& \\ 
scorep-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for scorep

% <-- begin entry for tau
tau-gnu-mpich-ohpc &
\multirow{3}{*}{2.27} & 
\multirow{7}{\linewidth}{Tuning and Analysis Utilities Profiling Package. \newline {\color{logoblue} \url{http://www.cs.uoregon.edu/research/tau/home.php}}} \\ 
tau-gnu-openmpi-ohpc &
& \\ 
tau-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} tau-gnu7-mpich-ohpc &\multirow{3}{*}{2.27.1}
& \\ 
tau-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} tau-gnu8-mpich-ohpc &\multirow{2}{*}{2.28}
& \\ 
tau-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for tau

\bottomrule
\end{tabularx}
