\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{r|X}
\toprule
{\bf Group Name} & {\bf Description} \\ 
\midrule

fsp-adios & FSP adios IO library builds for various compiler/MPI combinations. \\ 
fsp-autotools & Collection of GNU autotools packages. \\ 
fsp-base & FSP base packages. \\ 
fsp-boost & FSP Boost library builds for various compiler/MPI combinations. \\ 
fsp-fftw & FSP FFTW library builds for various compiler/MPI combinations. \\ 
fsp-gsl & ForestPeak GSL library builds for various compiler combinations. \\ 
fsp-hdf5 & FSP HDF5 library builds for various compiler combinations. \\ 
fsp-hypre & FSP Hypre library builds for various compiler/MPI combinations. \\ 
fsp-imb & FSP builds for Intel IMB MPI benchmarks. \\ 
fsp-metis & ForestPeak METIS library builds for various compiler combinations. \\ 
fsp-mpiP & FSP mpiP profiling library builds for various compiler/MPI combinations. \\ 
fsp-mumps & FSP Mumps library builds for various compiler/MPI combinations. \\ 
fsp-netcdf & FSP NetCDF library builds for various compiler/MPI combinations. \\ 
fsp-numpy & ForestPeak Numpy python module builds for various compiler combinations. \\ 
fsp-petsc & FSP PETSC library builds for various compiler/MPI combinations. \\ 
fsp-phdf5 & FSP HDF5 parallel library builds for various compiler/MPI combinations. \\ 
fsp-scipy & FSP Scientific Python library builds for various compiler/MPI combinations. \\ 
fsp-slurm-client & FSP client packages for SLURM. \\ 
fsp-slurm-server & FSP server packages for SLURM. \\ 
fsp-superlu\_dist & FSP Superlu\_dist library builds for various compiler/MPI combinations. \\ 
fsp-tau & FSP TAU library builds for various compiler/MPI combinations. \\ 
fsp-trilinos & FSP Trilinos library builds for various compiler/MPI combinations. \\ 
fsp-warewulf & Base packages for Warewulf provisioning. \\ 
\bottomrule
\end{tabularx}
