\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for clustershell-ohpc
\multirow{2}{*}{clustershell-ohpc} & 
\multirow{2}{*}{1.8} & 
Python framework for efficient cluster administration. \newline { \color{logoblue} \url{http://clustershell.sourceforge.net}} 
\\ \hline 
% <-- end entry for clustershell-ohpc

% <-- begin entry for conman-ohpc
\multirow{2}{*}{conman-ohpc} & 
\multirow{2}{*}{0.3.0} & 
ConMan: The Console Manager. \newline { \color{logoblue} \url{http://dun.github.io/conman}} 
\\ \hline 
% <-- end entry for conman-ohpc

% <-- begin entry for docs-ohpc
\multirow{2}{*}{docs-ohpc} & 
\multirow{2}{*}{1.3.7} & 
OpenHPC documentation. \newline { \color{logoblue} \url{https://github.com/openhpc/ohpc}} 
\\ \hline 
% <-- end entry for docs-ohpc

% <-- begin entry for examples-ohpc
\multirow{2}{*}{examples-ohpc} & 
\multirow{2}{*}{1.5} & 
Example source code and templates for use within OpenHPC environment.  { \color{logoblue} \url{https://github.com/openhpc/ohpc}} 
\\ \hline 
% <-- end entry for examples-ohpc

% <-- begin entry for ganglia-ohpc
\multirow{2}{*}{ganglia-ohpc} & 
\multirow{2}{*}{3.7.2} & 
Distributed Monitoring System. \newline { \color{logoblue} \url{http://ganglia.sourceforge.net}} 
\\ \hline 
% <-- end entry for ganglia-ohpc

% <-- begin entry for genders-ohpc
\multirow{2}{*}{genders-ohpc} & 
\multirow{2}{*}{1.22} & 
Static cluster configuration database. \newline { \color{logoblue} \url{https://github.com/chaos/genders}} 
\\ \hline 
% <-- end entry for genders-ohpc

% <-- begin entry for lmod-defaults
lmod-defaults-gnu7-impi-ohpc &
\multirow{8}{*}{1.3.1} & 
\multirow{14}{\linewidth}{OpenHPC default login environments. \newline {\color{logoblue} \url{https://github.com/openhpc/ohpc}}} \\ 
lmod-defaults-gnu7-mpich-ohpc &
& \\ 
lmod-defaults-gnu7-mvapich2-ohpc &
& \\ 
lmod-defaults-gnu7-openmpi-ohpc &
& \\ 
lmod-defaults-intel-impi-ohpc &
& \\ 
lmod-defaults-intel-mpich-ohpc &
& \\ 
lmod-defaults-intel-mvapich2-ohpc &
& \\ 
lmod-defaults-intel-openmpi-ohpc &
& \\ 
\cline{1-2} lmod-defaults-gnu7-openmpi3-ohpc &\multirow{6}{*}{1.3.3}
& \\ 
lmod-defaults-gnu8-impi-ohpc &
& \\ 
lmod-defaults-gnu8-mpich-ohpc &
& \\ 
lmod-defaults-gnu8-mvapich2-ohpc &
& \\ 
lmod-defaults-gnu8-openmpi3-ohpc &
& \\ 
lmod-defaults-intel-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for lmod-defaults

% <-- begin entry for lmod-ohpc
\multirow{2}{*}{lmod-ohpc} & 
\multirow{2}{*}{7.8.15} & 
Lua based Modules (lmod). \newline { \color{logoblue} \url{https://github.com/TACC/Lmod}} 
\\ \hline 
% <-- end entry for lmod-ohpc

% <-- begin entry for losf-ohpc
\multirow{2}{*}{losf-ohpc} & 
\multirow{2}{*}{0.56.0} & 
A Linux operating system framework for managing HPC clusters.  { \color{logoblue} \url{https://github.com/hpcsi/losf}} 
\\ \hline 
% <-- end entry for losf-ohpc

% <-- begin entry for mrsh-ohpc
\multirow{2}{*}{mrsh-ohpc} & 
\multirow{2}{*}{2.12} & 
Remote shell program that uses munge authentication. \newline { \color{logoblue} \url{https://github.com/chaos/mrsh}} 
\\ \hline 
% <-- end entry for mrsh-ohpc

% <-- begin entry for nagios-plugins-ohpc
\multirow{2}{*}{nagios-plugins-ohpc} & 
\multirow{2}{*}{2.2.1} & 
Host/service/network monitoring program plugins for Nagios. \newline { \color{logoblue} \url{https://www.nagios-plugins.org}} 
\\ \hline 
% <-- end entry for nagios-plugins-ohpc

% <-- begin entry for nagios-ohpc
\multirow{2}{*}{nagios-ohpc} & 
\multirow{2}{*}{4.4.3} & 
Host/service/network monitoring program. \newline { \color{logoblue} \url{http://www.nagios.org}} 
\\ \hline 
% <-- end entry for nagios-ohpc

% <-- begin entry for ndoutils-ohpc
\multirow{2}{*}{ndoutils-ohpc} & 
\multirow{2}{*}{2.1.3} & 
Stores all configuration and event data from Nagios in a database.  { \color{logoblue} \url{http://www.nagios.org/download/addons}} 
\\ \hline 
% <-- end entry for ndoutils-ohpc

% <-- begin entry for nhc-ohpc
\multirow{2}{*}{nhc-ohpc} & 
\multirow{2}{*}{1.4.2} & 
LBNL Node Health Check. \newline { \color{logoblue} \url{https://github.com/mej/nhc}} 
\\ \hline 
% <-- end entry for nhc-ohpc

% <-- begin entry for nrpe-ohpc
\multirow{2}{*}{nrpe-ohpc} & 
\multirow{2}{*}{3.2.0} & 
Host/service/network monitoring agent for Nagios. \newline { \color{logoblue} \url{http://www.nagios.org}} 
\\ \hline 
% <-- end entry for nrpe-ohpc

% <-- begin entry for ohpc-release
\multirow{2}{*}{ohpc-release} & 
\multirow{2}{*}{1.3} & 
OpenHPC release files. \newline { \color{logoblue} \url{https://github.com/openhpc/ohpc}} 
\\ \hline 
% <-- end entry for ohpc-release

% <-- begin entry for pdsh-ohpc
\multirow{2}{*}{pdsh-ohpc} & 
\multirow{2}{*}{2.33} & 
Parallel remote shell program. \newline { \color{logoblue} \url{https://github.com/chaos/pdsh}} 
\\ \hline 
% <-- end entry for pdsh-ohpc

% <-- begin entry for prun-ohpc
\multirow{2}{*}{prun-ohpc} & 
\multirow{2}{*}{1.3} & 
Convenience utility for parallel job launch. \newline { \color{logoblue} \url{https://github.com/openhpc/ohpc}} 
\\ \hline 
% <-- end entry for prun-ohpc

% <-- begin entry for test-suite-ohpc
\multirow{2}{*}{test-suite-ohpc} & 
\multirow{2}{*}{1.3.7} & 
Integration test suite for OpenHPC. \newline { \color{logoblue} \url{https://github.com/openhpc/ohpc/tests}} 
\\ \hline 
% <-- end entry for test-suite-ohpc

\bottomrule
\end{tabularx}
