\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcolumntype{L}[1]{>{\raggedleft}p{#1}}
\small
\begin{tabularx}{\textwidth}{r|X}
\toprule
{\bf Group Name} & {\bf Description} \\
\midrule

ohpc-autotools & Collection of GNU autotools packages. \\
\hline
ohpc-base & Collection of base packages. \\
\hline
ohpc-base-compute & Collection of compute node base packages. \\
\hline
ohpc-gnu12-geopm & Global Extensible Open Power Manager for use with GNU compiler toolchain. \\
\hline
ohpc-gnu12-io-libs & Collection of IO library builds for use with GNU compiler toolchain. \\
\hline
ohpc-gnu12-mpich-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the MPICH runtime. \\
\hline
ohpc-gnu12-mpich-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the MPICH runtime. \\
\hline
ohpc-gnu12-mpich-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the MPICH runtime. \\
\hline
ohpc-gnu12-mvapich2-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the MVAPICH2 runtime. \\
\hline
ohpc-gnu12-mvapich2-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the MVAPICH2 runtime. \\
\hline
ohpc-gnu12-mvapich2-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the MVAPICH2 runtime. \\
\hline
ohpc-gnu12-openmpi4-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\
\hline
ohpc-gnu12-openmpi4-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\
\hline
ohpc-gnu12-openmpi4-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the OpenMPI runtime. \\
\hline
ohpc-gnu12-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain. \\
\hline
ohpc-gnu12-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain. \\
\hline
ohpc-gnu12-python-libs & Collection of python related library builds for use with GNU compiler toolchain. \\
\hline
ohpc-gnu12-python3-libs & Collection of python3 related library builds for use with GNU compiler toolchain. \\
\hline
ohpc-gnu12-runtimes & Collection of runtimes for use with GNU compiler toolchain. \\
\hline
ohpc-gnu12-serial-libs & Collection of serial library builds for use with GNU compiler toolchain. \\
\hline
ohpc-intel-geopm & Global Extensible Open Power Manager for use with Intel(R) oneAPI Toolkit. \\
\hline
ohpc-intel-impi-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit and Intel(R) MPI runtime. \\
\hline
ohpc-intel-impi-parallel-libs & Collection of parallel library builds for use with Intel(R) oneAPI Toolkit and the Intel(R) MPI Library. \\
\hline
ohpc-intel-impi-perf-tools & Collection of performance tool builds for use with Intel(R) oneAPI Toolkit compiler toolchain and the Intel(R) MPI runtime. \\
\hline
ohpc-intel-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit. \\
\hline
ohpc-intel-mpich-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit and MPICH runtime. \\
\hline
ohpc-intel-mpich-parallel-libs & Collection of parallel library builds for use with Intel(R) oneAPI Toolkit and the MPICH runtime. \\
\hline
ohpc-intel-mpich-perf-tools & Collection of performance tool builds for use with Intel(R) oneAPI Toolkit compiler toolchain and the MPICH runtime. \\
\hline
ohpc-intel-mvapich2-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit and MVAPICH2 runtime. \\
\hline
\bottomrule
\end{tabularx}
