\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

likwid-gnu9-ohpc &
\multirow{1}{*}{5.0.1} & 
\multirow{3}{\linewidth}{Performance tools for the Linux console. \newline {\color{logoblue} \url{https://github.com/RRZE-HPC/likwid}}} \\ 
\cline{1-2} likwid-gnu12-ohpc &\multirow{2}{*}{5.2.2}
& \\ 
likwid-intel-ohpc &
& \\ 
\hline
% <-- end entry for likwid

% <-- begin entry for msr-safe-ohpc
\multirow{2}{*}{msr-safe-ohpc} & 
\multirow{2}{*}{1.6.0} & 
Allows safer access to model specific registers (MSRs). \newline { \color{logoblue} \url{https://github.com/LLNL/msr-safe}} 
\\ \hline 
% <-- end entry for msr-safe-ohpc

% <-- begin entry for omb
omb-gnu9-impi-ohpc &
\multirow{4}{*}{5.8} & 
\multirow{12}{\linewidth}{OSU Micro-benchmarks. \newline {\color{logoblue} \url{http://mvapich.cse.ohio-state.edu/benchmarks}}} \\ 
omb-gnu9-mpich-ohpc &
& \\ 
omb-gnu9-mvapich2-ohpc &
& \\ 
omb-gnu9-openmpi4-ohpc &
& \\ 
\cline{1-2} omb-gnu12-impi-ohpc &\multirow{8}{*}{6.1}
& \\ 
omb-gnu12-mpich-ohpc &
& \\ 
omb-gnu12-mvapich2-ohpc &
& \\ 
omb-gnu12-openmpi4-ohpc &
& \\ 
omb-intel-impi-ohpc &
& \\ 
omb-intel-mpich-ohpc &
& \\ 
omb-intel-mvapich2-ohpc &
& \\ 
omb-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for omb

% <-- begin entry for paraver-ohpc
\multirow{2}{*}{paraver-ohpc} & 
\multirow{2}{*}{4.10.4} & 
Paraver. \newline { \color{logoblue} \url{https://tools.bsc.es}} 
\\ \hline 
% <-- end entry for paraver-ohpc

% <-- begin entry for papi-ohpc
\multirow{2}{*}{papi-ohpc} & 
\multirow{2}{*}{6.0.0} & 
Performance Application Programming Interface. \newline { \color{logoblue} \url{http://icl.cs.utk.edu/papi}} 
\\ \hline 
% <-- end entry for papi-ohpc

% <-- begin entry for pdtoolkit
pdtoolkit-gnu12-ohpc &
\multirow{3}{*}{3.25.1} & 
\multirow{3}{\linewidth}{PDT is a framework for analyzing source code. \newline {\color{logoblue} \url{http://www.cs.uoregon.edu/Research/pdt}}} \\ 
pdtoolkit-gnu9-ohpc &
& \\ 
pdtoolkit-intel-ohpc &
& \\ 
\hline
% <-- end entry for pdtoolkit

% <-- begin entry for scalasca
scalasca-gnu12-impi-ohpc &
\multirow{12}{*}{2.5} & 
\multirow{12}{\linewidth}{Toolset for performance analysis of large-scale parallel applications. \newline {\color{logoblue} \url{http://www.scalasca.org}}} \\ 
scalasca-gnu12-mpich-ohpc &
& \\ 
scalasca-gnu12-mvapich2-ohpc &
& \\ 
scalasca-gnu12-openmpi4-ohpc &
& \\ 
scalasca-gnu9-impi-ohpc &
& \\ 
scalasca-gnu9-mpich-ohpc &
& \\ 
scalasca-gnu9-mvapich2-ohpc &
& \\ 
scalasca-gnu9-openmpi4-ohpc &
& \\ 
scalasca-intel-impi-ohpc &
& \\ 
scalasca-intel-mpich-ohpc &
& \\ 
scalasca-intel-mvapich2-ohpc &
& \\ 
scalasca-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for scalasca

% <-- begin entry for scorep
scorep-gnu9-impi-ohpc &
\multirow{4}{*}{6.0} & 
\multirow{12}{\linewidth}{Scalable Performance Measurement Infrastructure for Parallel Codes. \newline {\color{logoblue} \url{http://www.vi-hps.org/projects/score-p}}} \\ 
scorep-gnu9-mpich-ohpc &
& \\ 
scorep-gnu9-mvapich2-ohpc &
& \\ 
scorep-gnu9-openmpi4-ohpc &
& \\ 
\cline{1-2} scorep-gnu12-impi-ohpc &\multirow{8}{*}{7.1}
& \\ 
scorep-gnu12-mpich-ohpc &
& \\ 
scorep-gnu12-mvapich2-ohpc &
& \\ 
scorep-gnu12-openmpi4-ohpc &
& \\ 
scorep-intel-impi-ohpc &
& \\ 
scorep-intel-mpich-ohpc &
& \\ 
scorep-intel-mvapich2-ohpc &
& \\ 
scorep-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for scorep

% <-- begin entry for tau
\bottomrule
\end{tabularx}
