\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{r|X}
\toprule
{\bf Group Name} & {\bf Description} \\ 
\midrule

ohpc-intel-mvapich2-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite and MVAPICH2 runtime. \\ 
\hline
ohpc-intel-mvapich2-parallel-libs & Collection of parallel library builds for use with Intel(R) Parallel Studio XE toolchain and the MVAPICH2 runtime. \\ 
\hline
ohpc-intel-mvapich2-perf-tools & Collection of performance tool builds for use with Intel(R) Parallel Studio XE compiler toolchain and the MVAPICH2 runtime. \\ 
\hline
ohpc-intel-openmpi4-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite and OpenMPI runtime. \\ 
\hline
ohpc-intel-openmpi4-parallel-libs & Collection of parallel library builds for use with Intel(R) Parallel Studio XE toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-intel-openmpi4-perf-tools & Collection of performance tool builds for use with Intel(R) Parallel Studio XE compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-intel-perf-tools & Collection of performance tool builds for use with Intel(R) Parallel Studio XE toolchain. \\ 
\hline
ohpc-intel-python3-libs & Collection of python3 related library builds for use with Intel(R) Parallel Studio XE toolchain. \\ 
\hline
ohpc-intel-runtimes & Collection of runtimes for use with Intel(R) Parallel Studio XE toolchain. \\ 
\hline
ohpc-intel-serial-libs & Collection of serial library builds for use with Intel(R) Parallel Studio XE toolchain. \\ 
\hline
ohpc-slurm-client & Collection of client packages for SLURM. \\ 
\hline
ohpc-slurm-server & Collection of server packages for SLURM. \\ 
\hline
ohpc-warewulf & Collection of base packages for Warewulf provisioning. \\ 
\hline
\bottomrule
\end{tabularx}
