\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for dimemas
dimemas-gnu9-impi-ohpc &
\multirow{8}{*}{5.4.2} & 
\multirow{8}{\linewidth}{Dimemas tool. \newline {\color{logoblue} \url{https://tools.bsc.es}}} \\ 
dimemas-gnu9-mpich-ohpc &
& \\ 
dimemas-gnu9-mvapich2-ohpc &
& \\ 
dimemas-gnu9-openmpi4-ohpc &
& \\ 
dimemas-intel-impi-ohpc &
& \\ 
dimemas-intel-mpich-ohpc &
& \\ 
dimemas-intel-mvapich2-ohpc &
& \\ 
dimemas-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for dimemas

% <-- begin entry for extrae
extrae-gnu9-impi-ohpc &
\multirow{8}{*}{3.7.0} & 
\multirow{8}{\linewidth}{Extrae tool. \newline {\color{logoblue} \url{https://tools.bsc.es}}} \\ 
extrae-gnu9-mpich-ohpc &
& \\ 
extrae-gnu9-mvapich2-ohpc &
& \\ 
extrae-gnu9-openmpi4-ohpc &
& \\ 
extrae-intel-impi-ohpc &
& \\ 
extrae-intel-mpich-ohpc &
& \\ 
extrae-intel-mvapich2-ohpc &
& \\ 
extrae-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for extrae

% <-- begin entry for geopm
geopm-gnu9-impi-ohpc &
\multirow{8}{*}{1.1.0} & 
\multirow{8}{\linewidth}{Global Extensible Open Power Manager. \newline {\color{logoblue} \url{https://geopm.github.io}}} \\ 
geopm-gnu9-mpich-ohpc &
& \\ 
geopm-gnu9-mvapich2-ohpc &
& \\ 
geopm-gnu9-openmpi4-ohpc &
& \\ 
geopm-intel-impi-ohpc &
& \\ 
geopm-intel-mpich-ohpc &
& \\ 
geopm-intel-mvapich2-ohpc &
& \\ 
geopm-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for geopm

% <-- begin entry for imb
imb-gnu9-impi-ohpc &
\multirow{8}{*}{2019.6} & 
\multirow{8}{\linewidth}{Intel MPI Benchmarks (IMB). \newline {\color{logoblue} \url{https://software.intel.com/en-us/articles/intel-mpi-benchmarks}}} \\ 
imb-gnu9-mpich-ohpc &
& \\ 
imb-gnu9-mvapich2-ohpc &
& \\ 
imb-gnu9-openmpi4-ohpc &
& \\ 
imb-intel-impi-ohpc &
& \\ 
imb-intel-mpich-ohpc &
& \\ 
imb-intel-mvapich2-ohpc &
& \\ 
imb-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for imb

% <-- begin entry for likwid
likwid-gnu9-ohpc &
\multirow{2}{*}{5.0.1} & 
\multirow{2}{\linewidth}{Performance tools for the Linux console. \newline {\color{logoblue} \url{https://github.com/RRZE-HPC/likwid}}} \\ 
likwid-intel-ohpc &
& \\ 
\hline
% <-- end entry for likwid

% <-- begin entry for msr-safe-ohpc
\multirow{2}{*}{msr-safe-ohpc} & 
\multirow{2}{*}{1.6.0} & 
Allows safer access to model specific registers (MSRs). \newline { \color{logoblue} \url{https://github.com/LLNL/msr-safe}} 
\\ \hline 
% <-- end entry for msr-safe-ohpc

% <-- begin entry for omb
omb-gnu9-impi-ohpc &
\multirow{8}{*}{5.8} & 
\multirow{8}{\linewidth}{OSU Micro-benchmarks. \newline {\color{logoblue} \url{http://mvapich.cse.ohio-state.edu/benchmarks}}} \\ 
omb-gnu9-mpich-ohpc &
& \\ 
omb-gnu9-mvapich2-ohpc &
& \\ 
omb-gnu9-openmpi4-ohpc &
& \\ 
omb-intel-impi-ohpc &
& \\ 
omb-intel-mpich-ohpc &
& \\ 
omb-intel-mvapich2-ohpc &
& \\ 
omb-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for omb

% <-- begin entry for paraver-ohpc
\multirow{2}{*}{paraver-ohpc} & 
\multirow{2}{*}{4.8.2} & 
Paraver. \newline { \color{logoblue} \url{https://tools.bsc.es}} 
\\ \hline 
% <-- end entry for paraver-ohpc

% <-- begin entry for papi-ohpc
\multirow{2}{*}{papi-ohpc} & 
\multirow{2}{*}{5.7.0} & 
Performance Application Programming Interface. \newline { \color{logoblue} \url{http://icl.cs.utk.edu/papi}} 
\\ \hline 
% <-- end entry for papi-ohpc

% <-- begin entry for pdtoolkit
\bottomrule
\end{tabularx}
