\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcolumntype{L}[1]{>{\raggedleft}p{#1}}
\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcolumntype{L}[1]{>{\raggedleft}p{#1}}
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\
\midrule

% <-- begin entry for adios2
adios2-gnu12-impi-ohpc &
\multirow{13}{*}{2.8.3} &
\multirow{13}{\linewidth}{The Adaptable IO System v2 (ADIOS2). \newline {\color{logoblue} \url{https://adios2.readthedocs.io/en/latest/index.html}}}\\
adios2-gnu12-mpich-ohpc &
& \\
adios2-gnu12-mvapich2-ohpc &
& \\
adios2-gnu12-openmpi4-ohpc &
& \\
adios2-gnu13-impi-ohpc &
& \\
adios2-gnu13-mpich-ohpc &
& \\
adios2-gnu13-mvapich2-ohpc &
& \\
adios2-gnu13-openmpi5-ohpc &
& \\
adios2-intel-impi-ohpc &
& \\
adios2-intel-mpich-ohpc &
& \\
adios2-intel-mvapich2-ohpc &
& \\
adios2-intel-openmpi4-ohpc &
& \\
adios2-intel-openmpi5-ohpc &
& \\
\hline
% <-- end entry for adios2

% <-- begin entry for hdf5
hdf5-gnu12-ohpc &
\multirow{3}{*}{1.14.0} &
\multirow{3}{\linewidth}{A general purpose library and file format for storing scientific data. \newline {\color{logoblue} \url{http://www.hdfgroup.org/HDF5}}}\\
hdf5-gnu13-ohpc &
& \\
hdf5-intel-ohpc &
& \\
\hline
% <-- end entry for hdf5

% <-- begin entry for netcdf-cxx
netcdf-cxx-gnu12-impi-ohpc &
\multirow{7}{*}{4.3.1} &
\multirow{7}{\linewidth}{C++ Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}}\\
netcdf-cxx-gnu12-mpich-ohpc &
& \\
netcdf-cxx-gnu12-mvapich2-ohpc &
& \\
netcdf-cxx-gnu12-openmpi4-ohpc &
& \\
netcdf-cxx-gnu13-impi-ohpc &
& \\
netcdf-cxx-gnu13-mpich-ohpc &
& \\
netcdf-cxx-gnu13-mvapich2-ohpc &
& \\
\hline
% <-- end entry for netcdf-cxx

% <-- begin entry for netcdf-cxx
netcdf-cxx-gnu13-ohpc &
\multirow{8}{*}{4.3.1} &
\multirow{8}{\linewidth}{C++ Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}}\\
netcdf-cxx-gnu13-openmpi5-ohpc &
& \\
netcdf-cxx-intel-impi-ohpc &
& \\
netcdf-cxx-intel-mpich-ohpc &
& \\
netcdf-cxx-intel-mvapich2-ohpc &
& \\
netcdf-cxx-intel-ohpc &
& \\
netcdf-cxx-intel-openmpi4-ohpc &
& \\
netcdf-cxx-intel-openmpi5-ohpc &
& \\
\hline
% <-- end entry for netcdf-cxx

% <-- begin entry for netcdf-fortran
netcdf-fortran-gnu12-impi-ohpc &
\multirow{5}{*}{4.6.0} &
\multirow{8}{\linewidth}{Fortran Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}}\\
netcdf-fortran-gnu12-mpich-ohpc &
& \\
netcdf-fortran-gnu12-mvapich2-ohpc &
& \\
netcdf-fortran-gnu12-openmpi4-ohpc &
& \\
netcdf-fortran-intel-openmpi4-ohpc &
& \\
\cline{1-2} netcdf-fortran-gnu13-impi-ohpc &\multirow{3}{*}{4.6.1}
& \\
netcdf-fortran-gnu13-mpich-ohpc &
& \\
netcdf-fortran-gnu13-mvapich2-ohpc &
& \\
\hline
% <-- end entry for netcdf-fortran

% <-- begin entry for netcdf-fortran
netcdf-fortran-gnu13-ohpc &
\multirow{7}{*}{4.6.1} &
\multirow{7}{\linewidth}{Fortran Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}}\\
netcdf-fortran-gnu13-openmpi5-ohpc &
& \\
netcdf-fortran-intel-impi-ohpc &
& \\
netcdf-fortran-intel-mpich-ohpc &
& \\
netcdf-fortran-intel-mvapich2-ohpc &
& \\
netcdf-fortran-intel-ohpc &
& \\
netcdf-fortran-intel-openmpi5-ohpc &
& \\
\hline
% <-- end entry for netcdf-fortran

% <-- begin entry for netcdf
netcdf-gnu12-impi-ohpc &
\multirow{5}{*}{4.9.0} &
\multirow{8}{\linewidth}{C Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}}\\
netcdf-gnu12-mpich-ohpc &
& \\
netcdf-gnu12-mvapich2-ohpc &
& \\
netcdf-gnu12-openmpi4-ohpc &
& \\
netcdf-intel-openmpi4-ohpc &
& \\
\cline{1-2} netcdf-gnu13-impi-ohpc &\multirow{3}{*}{4.9.2}
& \\
netcdf-gnu13-mpich-ohpc &
& \\
netcdf-gnu13-mvapich2-ohpc &
& \\
\hline
% <-- end entry for netcdf

% <-- begin entry for netcdf
netcdf-gnu13-ohpc &
\multirow{7}{*}{4.9.2} &
\multirow{7}{\linewidth}{C Libraries for the Unidata network Common Data Form. \newline {\color{logoblue} \url{http://www.unidata.ucar.edu/software/netcdf}}}\\
netcdf-gnu13-openmpi5-ohpc &
& \\
netcdf-intel-impi-ohpc &
& \\
netcdf-intel-mpich-ohpc &
& \\
netcdf-intel-mvapich2-ohpc &
& \\
netcdf-intel-ohpc &
& \\
netcdf-intel-openmpi5-ohpc &
& \\
\hline
% <-- end entry for netcdf

% <-- begin entry for phdf5
phdf5-gnu12-impi-ohpc &
\multirow{13}{*}{1.14.0} &
\multirow{13}{\linewidth}{A general purpose library and file format for storing scientific data. \newline {\color{logoblue} \url{http://www.hdfgroup.org/HDF5}}}\\
phdf5-gnu12-mpich-ohpc &
& \\
phdf5-gnu12-mvapich2-ohpc &
& \\
phdf5-gnu12-openmpi4-ohpc &
& \\
phdf5-gnu13-impi-ohpc &
& \\
phdf5-gnu13-mpich-ohpc &
& \\
phdf5-gnu13-mvapich2-ohpc &
& \\
phdf5-gnu13-openmpi5-ohpc &
& \\
phdf5-intel-impi-ohpc &
& \\
phdf5-intel-mpich-ohpc &
& \\
phdf5-intel-mvapich2-ohpc &
& \\
phdf5-intel-openmpi4-ohpc &
& \\
phdf5-intel-openmpi5-ohpc &
& \\
\hline
% <-- end entry for phdf5

% <-- begin entry for pnetcdf
pnetcdf-gnu12-impi-ohpc &
\multirow{13}{*}{1.12.3} &
\multirow{13}{\linewidth}{A Parallel NetCDF library (PnetCDF). \newline {\color{logoblue} \url{http://cucis.ece.northwestern.edu/projects/PnetCDF}}}\\
pnetcdf-gnu12-mpich-ohpc &
& \\
pnetcdf-gnu12-mvapich2-ohpc &
& \\
pnetcdf-gnu12-openmpi4-ohpc &
& \\
\bottomrule
\end{tabularx}
