\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for boost
boost-gnu9-impi-ohpc &
\multirow{4}{*}{1.71.0} & 
\multirow{4}{\linewidth}{Boost free peer-reviewed portable C++ source libraries. \newline {\color{logoblue} \url{http://www.boost.org}}} \\ 
boost-gnu9-mpich-ohpc &
& \\ 
boost-gnu9-mvapich2-ohpc &
& \\ 
boost-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for boost

% <-- begin entry for fftw
fftw-gnu9-impi-ohpc &
\multirow{4}{*}{3.3.8} & 
\multirow{4}{\linewidth}{A Fast Fourier Transform library. \newline {\color{logoblue} \url{http://www.fftw.org}}} \\ 
fftw-gnu9-mpich-ohpc &
& \\ 
fftw-gnu9-mvapich2-ohpc &
& \\ 
fftw-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for fftw

% <-- begin entry for hypre
hypre-gnu9-impi-ohpc &
\multirow{8}{*}{2.18.1} & 
\multirow{8}{\linewidth}{Scalable algorithms for solving linear systems of equations. \newline {\color{logoblue} \url{http://www.llnl.gov/casc/hypre}}} \\ 
hypre-gnu9-mpich-ohpc &
& \\ 
hypre-gnu9-mvapich2-ohpc &
& \\ 
hypre-gnu9-openmpi4-ohpc &
& \\ 
hypre-intel-impi-ohpc &
& \\ 
hypre-intel-mpich-ohpc &
& \\ 
hypre-intel-mvapich2-ohpc &
& \\ 
hypre-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for hypre

% <-- begin entry for mfem
mfem-gnu9-impi-ohpc &
\multirow{8}{*}{4.0} & 
\multirow{8}{\linewidth}{Lightweight, general, scalable C++ library for finite element methods. \newline {\color{logoblue} \url{http://mfem.org}}} \\ 
mfem-gnu9-mpich-ohpc &
& \\ 
mfem-gnu9-mvapich2-ohpc &
& \\ 
mfem-gnu9-openmpi4-ohpc &
& \\ 
mfem-intel-impi-ohpc &
& \\ 
mfem-intel-mpich-ohpc &
& \\ 
mfem-intel-mvapich2-ohpc &
& \\ 
mfem-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for mfem

% <-- begin entry for mumps
mumps-gnu9-impi-ohpc &
\multirow{8}{*}{5.2.1} & 
\multirow{8}{\linewidth}{A MUltifrontal Massively Parallel Sparse direct Solver. \newline {\color{logoblue} \url{http://mumps.enseeiht.fr}}} \\ 
mumps-gnu9-mpich-ohpc &
& \\ 
mumps-gnu9-mvapich2-ohpc &
& \\ 
mumps-gnu9-openmpi4-ohpc &
& \\ 
mumps-intel-impi-ohpc &
& \\ 
mumps-intel-mpich-ohpc &
& \\ 
mumps-intel-mvapich2-ohpc &
& \\ 
mumps-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for mumps

% <-- begin entry for opencoarrays
opencoarrays-gnu9-impi-ohpc &
\multirow{4}{*}{2.8.0} & 
\multirow{4}{\linewidth}{ABI to leverage the parallel programming features of the Fortran 2018 DIS. \newline {\color{logoblue} \url{http://www.opencoarrays.org}}} \\ 
opencoarrays-gnu9-mpich-ohpc &
& \\ 
opencoarrays-gnu9-mvapich2-ohpc &
& \\ 
opencoarrays-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for opencoarrays

% <-- begin entry for petsc
petsc-gnu9-impi-ohpc &
\multirow{8}{*}{3.13.1} & 
\multirow{8}{\linewidth}{Portable Extensible Toolkit for Scientific Computation. \newline {\color{logoblue} \url{http://www.mcs.anl.gov/petsc}}} \\ 
petsc-gnu9-mpich-ohpc &
& \\ 
petsc-gnu9-mvapich2-ohpc &
& \\ 
petsc-gnu9-openmpi4-ohpc &
& \\ 
petsc-intel-impi-ohpc &
& \\ 
petsc-intel-mpich-ohpc &
& \\ 
petsc-intel-mvapich2-ohpc &
& \\ 
petsc-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for petsc

% <-- begin entry for ptscotch
ptscotch-gnu9-impi-ohpc &
\multirow{8}{*}{6.0.6} & 
\multirow{8}{\linewidth}{Graph, mesh and hypergraph partitioning library using MPI. \newline {\color{logoblue} \url{http://www.labri.fr/perso/pelegrin/scotch}}} \\ 
ptscotch-gnu9-mpich-ohpc &
& \\ 
ptscotch-gnu9-mvapich2-ohpc &
& \\ 
ptscotch-gnu9-openmpi4-ohpc &
& \\ 
ptscotch-intel-impi-ohpc &
& \\ 
ptscotch-intel-mpich-ohpc &
& \\ 
ptscotch-intel-mvapich2-ohpc &
& \\ 
ptscotch-intel-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for ptscotch

% <-- begin entry for scalapack
\bottomrule
\end{tabularx}
