\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{r|X}
\toprule
{\bf Group Name} & {\bf Description} \\ 
\midrule

ohpc-gnu9-openmpi4-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu9-openmpi4-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu9-openmpi4-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu9-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-python-libs & Collection of python related library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-python3-libs & Collection of python3 related library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-runtimes & Collection of runtimes for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu9-serial-libs & Collection of serial library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-intel-geopm & Global Extensible Open Power Manager for use with Intel(R) Parallel Studio XE software suite. \\ 
\hline
ohpc-intel-geopm & Global Extensible Open Power Manager for use with Intel(R) oneAPI Toolkit. \\ 
\hline
ohpc-intel-impi-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite and Intel(R) MPI runtime. \\ 
\hline
ohpc-intel-impi-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit and Intel(R) MPI runtime. \\ 
\hline
ohpc-intel-impi-parallel-libs & Collection of parallel library builds for use with Intel(R) Parallel Studio XE toolchain and the Intel(R) MPI Library. \\ 
\hline
ohpc-intel-impi-parallel-libs & Collection of parallel library builds for use with Intel(R) oneAPI Toolkit and the Intel(R) MPI Library. \\ 
\hline
ohpc-intel-impi-perf-tools & Collection of performance tool builds for use with Intel(R) Parallel Studio XE compiler toolchain and the Intel(R) MPI runtime. \\ 
\hline
ohpc-intel-impi-perf-tools & Collection of performance tool builds for use with Intel(R) oneAPI Toolkit compiler toolchain and the Intel(R) MPI runtime. \\ 
\hline
ohpc-intel-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite. \\ 
\hline
ohpc-intel-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit. \\ 
\hline
ohpc-intel-mpich-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite and MPICH runtime. \\ 
\hline
ohpc-intel-mpich-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit and MPICH runtime. \\ 
\hline
ohpc-intel-mpich-parallel-libs & Collection of parallel library builds for use with Intel(R) Parallel Studio XE toolchain and the MPICH runtime. \\ 
\hline
ohpc-intel-mpich-parallel-libs & Collection of parallel library builds for use with Intel(R) oneAPI Toolkit and the MPICH runtime. \\ 
\hline
ohpc-intel-mpich-perf-tools & Collection of performance tool builds for use with Intel(R) Parallel Studio XE compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-intel-mpich-perf-tools & Collection of performance tool builds for use with Intel(R) oneAPI Toolkit compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-intel-mvapich2-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite and MVAPICH2 runtime. \\ 
\hline
ohpc-intel-mvapich2-io-libs & Collection of IO library builds for use with Intel(R) oneAPI Toolkit and MVAPICH2 runtime. \\ 
\hline
\bottomrule
\end{tabularx}
