\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcolumntype{L}[1]{>{\raggedleft}p{#1}}
\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcolumntype{L}[1]{>{\raggedleft}p{#1}}
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\
\midrule

% <-- begin entry for boost
boost-gnu12-mpich-ohpc &
\multirow{6}{*}{1.81.0} &
\multirow{6}{\linewidth}{Free peer-reviewed portable C++ source libraries. \newline {\color{logoblue} \url{http://www.boost.org}}}\\
boost-gnu12-mvapich2-ohpc &
& \\
boost-gnu12-openmpi4-ohpc &
& \\
boost-gnu13-mpich-ohpc &
& \\
boost-gnu13-mvapich2-ohpc &
& \\
boost-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for boost

% <-- begin entry for fftw
fftw-gnu12-mpich-ohpc &
\multirow{6}{*}{3.3.10} &
\multirow{6}{\linewidth}{A Fast Fourier Transform library. \newline {\color{logoblue} \url{http://www.fftw.org}}}\\
fftw-gnu12-mvapich2-ohpc &
& \\
fftw-gnu12-openmpi4-ohpc &
& \\
fftw-gnu13-mpich-ohpc &
& \\
fftw-gnu13-mvapich2-ohpc &
& \\
fftw-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for fftw

% <-- begin entry for hypre
hypre-gnu12-mpich-ohpc &
\multirow{6}{*}{2.18.1} &
\multirow{6}{\linewidth}{Scalable algorithms for solving linear systems of equations. \newline {\color{logoblue} \url{http://www.llnl.gov/casc/hypre}}}\\
hypre-gnu12-mvapich2-ohpc &
& \\
hypre-gnu12-openmpi4-ohpc &
& \\
hypre-gnu13-mpich-ohpc &
& \\
hypre-gnu13-mvapich2-ohpc &
& \\
hypre-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for hypre

% <-- begin entry for mfem
mfem-gnu12-mpich-ohpc &
\multirow{6}{*}{4.4} &
\multirow{6}{\linewidth}{Lightweight, general, scalable C++ library for finite element methods. \newline {\color{logoblue} \url{http://mfem.org}}}\\
mfem-gnu12-mvapich2-ohpc &
& \\
mfem-gnu12-openmpi4-ohpc &
& \\
mfem-gnu13-mpich-ohpc &
& \\
mfem-gnu13-mvapich2-ohpc &
& \\
mfem-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for mfem

% <-- begin entry for mumps
mumps-gnu12-mpich-ohpc &
\multirow{6}{*}{5.2.1} &
\multirow{6}{\linewidth}{A MUltifrontal Massively Parallel Sparse direct Solver. \newline {\color{logoblue} \url{http://graal.ens-lyon.fr/MUMPS}}}\\
mumps-gnu12-mvapich2-ohpc &
& \\
mumps-gnu12-openmpi4-ohpc &
& \\
mumps-gnu13-mpich-ohpc &
& \\
mumps-gnu13-mvapich2-ohpc &
& \\
mumps-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for mumps

% <-- begin entry for opencoarrays
opencoarrays-gnu12-mpich-ohpc &
\multirow{6}{*}{2.10.0} &
\multirow{6}{\linewidth}{ABI to leverage the parallel programming features of the Fortran 2018 DIS. \newline {\color{logoblue} \url{http://www.opencoarrays.org}}}\\
opencoarrays-gnu12-mvapich2-ohpc &
& \\
opencoarrays-gnu12-openmpi4-ohpc &
& \\
opencoarrays-gnu13-mpich-ohpc &
& \\
opencoarrays-gnu13-mvapich2-ohpc &
& \\
opencoarrays-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for opencoarrays

% <-- begin entry for petsc
petsc-gnu12-mpich-ohpc &
\multirow{6}{*}{3.18.1} &
\multirow{6}{\linewidth}{Portable Extensible Toolkit for Scientific Computation. \newline {\color{logoblue} \url{http://www.mcs.anl.gov/petsc}}}\\
petsc-gnu12-mvapich2-ohpc &
& \\
petsc-gnu12-openmpi4-ohpc &
& \\
petsc-gnu13-mpich-ohpc &
& \\
petsc-gnu13-mvapich2-ohpc &
& \\
petsc-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for petsc

% <-- begin entry for ptscotch
ptscotch-gnu12-mpich-ohpc &
\multirow{6}{*}{7.0.1} &
\multirow{6}{\linewidth}{Graph, mesh and hypergraph partitioning library using MPI. \newline {\color{logoblue} \url{http://www.labri.fr/perso/pelegrin/scotch}}}\\
ptscotch-gnu12-mvapich2-ohpc &
& \\
ptscotch-gnu12-openmpi4-ohpc &
& \\
ptscotch-gnu13-mpich-ohpc &
& \\
ptscotch-gnu13-mvapich2-ohpc &
& \\
ptscotch-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for ptscotch

% <-- begin entry for scalapack
scalapack-gnu12-mpich-ohpc &
\multirow{6}{*}{2.2.0} &
\multirow{6}{\linewidth}{A subset of LAPACK routines redesigned for heterogeneous computing. \newline {\color{logoblue} \url{https://netlib.org/scalapack}}}\\
scalapack-gnu12-mvapich2-ohpc &
& \\
scalapack-gnu12-openmpi4-ohpc &
& \\
scalapack-gnu13-mpich-ohpc &
& \\
scalapack-gnu13-mvapich2-ohpc &
& \\
scalapack-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for scalapack

% <-- begin entry for slepc
slepc-gnu12-mpich-ohpc &
\multirow{6}{*}{3.18.0} &
\multirow{6}{\linewidth}{A library for solving large scale sparse eigenvalue problems. \newline {\color{logoblue} \url{http://slepc.upv.es}}}\\
slepc-gnu12-mvapich2-ohpc &
& \\
slepc-gnu12-openmpi4-ohpc &
& \\
slepc-gnu13-mpich-ohpc &
& \\
slepc-gnu13-mvapich2-ohpc &
& \\
slepc-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for slepc

% <-- begin entry for superlu_dist
superlu\_dist-gnu12-mpich-ohpc &
\multirow{6}{*}{6.4.0} &
\multirow{6}{\linewidth}{A general purpose library for the direct solution of linear equations. \newline {\color{logoblue} \url{https://portal.nersc.gov/project/sparse/superlu}}}\\
superlu\_dist-gnu12-mvapich2-ohpc &
& \\
superlu\_dist-gnu12-openmpi4-ohpc &
& \\
superlu\_dist-gnu13-mpich-ohpc &
& \\
superlu\_dist-gnu13-mvapich2-ohpc &
& \\
superlu\_dist-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for superlu_dist

% <-- begin entry for trilinos
trilinos-gnu12-mpich-ohpc &
\multirow{6}{*}{13.4.0} &
\multirow{6}{\linewidth}{A collection of libraries of numerical algorithms. \newline {\color{logoblue} \url{https://trilinos.org}}}\\
trilinos-gnu12-mvapich2-ohpc &
& \\
trilinos-gnu12-openmpi4-ohpc &
& \\
trilinos-gnu13-mpich-ohpc &
& \\
trilinos-gnu13-mvapich2-ohpc &
& \\
trilinos-gnu13-openmpi5-ohpc &
& \\
\hline
% <-- end entry for trilinos

\bottomrule
\end{tabularx}
