\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for EasyBuild-ohpc
\multirow{2}{*}{EasyBuild-ohpc} & 
\multirow{2}{*}{3.8.1} & 
Build and installation framework. \newline { \color{logoblue} \url{http://easybuilders.github.io/easybuild}} 
\\ \hline 
% <-- end entry for EasyBuild-ohpc

% <-- begin entry for automake-ohpc
\multirow{2}{*}{automake-ohpc} & 
\multirow{2}{*}{1.16.1} & 
A GNU tool for automatically creating Makefiles. \newline { \color{logoblue} \url{http://www.gnu.org/software/automake}} 
\\ \hline 
% <-- end entry for automake-ohpc

% <-- begin entry for autoconf-ohpc
\multirow{2}{*}{autoconf-ohpc} & 
\multirow{2}{*}{2.69} & 
A GNU tool for automatically configuring source code. \newline { \color{logoblue} \url{http://www.gnu.org/software/autoconf}} 
\\ \hline 
% <-- end entry for autoconf-ohpc

% <-- begin entry for cmake-ohpc
\multirow{2}{*}{cmake-ohpc} & 
\multirow{2}{*}{3.13.4} & 
CMake is an open-source, cross-platform family of tools designed to build, test and package software.  { \color{logoblue} \url{https://cmake.org}} 
\\ \hline 
% <-- end entry for cmake-ohpc

% <-- begin entry for hwloc-ohpc
\multirow{2}{*}{hwloc-ohpc} & 
\multirow{2}{*}{2.0.3} & 
Portable Hardware Locality. \newline { \color{logoblue} \url{http://www.open-mpi.org/projects/hwloc}} 
\\ \hline 
% <-- end entry for hwloc-ohpc

% <-- begin entry for libtool-ohpc
\multirow{2}{*}{libtool-ohpc} & 
\multirow{2}{*}{2.4.6} & 
The GNU Portable Library Tool. \newline { \color{logoblue} \url{http://www.gnu.org/software/libtool}} 
\\ \hline 
% <-- end entry for libtool-ohpc

% <-- begin entry for python-scipy
python-scipy-gnu-mpich-ohpc &
\multirow{3}{*}{0.19.1} & 
\multirow{5}{\linewidth}{Scientific Tools for Python. \newline {\color{logoblue} \url{http://www.scipy.org}}} \\ 
python-scipy-gnu-openmpi-ohpc &
& \\ 
python-scipy-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} python-scipy-gnu7-mpich-ohpc &\multirow{2}{*}{1.1.0}
& \\ 
python-scipy-gnu7-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for python-scipy

% <-- begin entry for python3-scipy
python3-scipy-gnu7-mpich-ohpc &
\multirow{2}{*}{1.1.0} & 
\multirow{2}{\linewidth}{Scientific Tools for Python. \newline {\color{logoblue} \url{http://www.scipy.org}}} \\ 
python3-scipy-gnu7-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for python3-scipy

% <-- begin entry for python-scipy
python-scipy-gnu8-mpich-ohpc &
\multirow{2}{*}{1.2.1} & 
\multirow{2}{\linewidth}{Scientific Tools for Python. \newline {\color{logoblue} \url{http://www.scipy.org}}} \\ 
python-scipy-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for python-scipy

% <-- begin entry for python3-scipy
python3-scipy-gnu8-mpich-ohpc &
\multirow{2}{*}{1.2.1} & 
\multirow{2}{\linewidth}{Scientific Tools for Python. \newline {\color{logoblue} \url{http://www.scipy.org}}} \\ 
python3-scipy-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for python3-scipy

% <-- begin entry for python-numpy
python-numpy-gnu-ohpc &
\multirow{1}{*}{1.12.1} & 
\multirow{2}{\linewidth}{NumPy array processing for numbers, strings, records and objects.  {\color{logoblue} \url{http://sourceforge.net/projects/numpy}}} \\ 
\cline{1-2} python-numpy-gnu7-ohpc &\multirow{1}{*}{1.14.3}
& \\ 
\hline
% <-- end entry for python-numpy

% <-- begin entry for python3-numpy
\multirow{2}{*}{python3-numpy-gnu7-ohpc} &
\multirow{2}{*}{1.14.3} & 
NumPy array processing for numbers, strings, records and objects.  {\color{logoblue} \url{http://sourceforge.net/projects/numpy}} \\ 
\hline
% <-- end entry for python3-numpy

% <-- begin entry for python-numpy
\multirow{2}{*}{python-numpy-gnu8-ohpc} &
\multirow{2}{*}{1.15.3} & 
NumPy array processing for numbers, strings, records and objects.  {\color{logoblue} \url{http://sourceforge.net/projects/numpy}} \\ 
\hline
% <-- end entry for python-numpy

% <-- begin entry for python3-numpy
\multirow{2}{*}{python3-numpy-gnu8-ohpc} &
\multirow{2}{*}{1.15.3} & 
NumPy array processing for numbers, strings, records and objects.  {\color{logoblue} \url{http://sourceforge.net/projects/numpy}} \\ 
\hline
% <-- end entry for python3-numpy

% <-- begin entry for python-mpi4py
python-mpi4py-gnu7-mpich-ohpc &
\multirow{4}{*}{3.0.0} & 
\multirow{4}{\linewidth}{Python bindings for the Message Passing Interface (MPI) standard. \newline {\color{logoblue} \url{https://bitbucket.org/mpi4py/mpi4py}}} \\ 
python-mpi4py-gnu7-openmpi3-ohpc &
& \\ 
python-mpi4py-gnu8-mpich-ohpc &
& \\ 
python-mpi4py-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for python-mpi4py

% <-- begin entry for python3-mpi4py
python3-mpi4py-gnu7-mpich-ohpc &
\multirow{4}{*}{3.0.0} & 
\multirow{4}{\linewidth}{Python bindings for the Message Passing Interface (MPI) standard. \newline {\color{logoblue} \url{https://bitbucket.org/mpi4py/mpi4py}}} \\ 
python3-mpi4py-gnu7-openmpi3-ohpc &
& \\ 
python3-mpi4py-gnu8-mpich-ohpc &
& \\ 
python3-mpi4py-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for python3-mpi4py

% <-- begin entry for spack-ohpc
\multirow{2}{*}{spack-ohpc} & 
\multirow{2}{*}{0.12.1} & 
HPC software package management. \newline { \color{logoblue} \url{https://github.com/LLNL/spack}} 
\\ \hline 
% <-- end entry for spack-ohpc

% <-- begin entry for valgrind-ohpc
\multirow{2}{*}{valgrind-ohpc} & 
\multirow{2}{*}{3.14.0} & 
Valgrind Memory Debugger. \newline { \color{logoblue} \url{http://www.valgrind.org}} 
\\ \hline 
% <-- end entry for valgrind-ohpc

\bottomrule
\end{tabularx}
