\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for boost
boost-gnu-mpich-ohpc &
\multirow{3}{*}{1.66.0} & 
\multirow{7}{\linewidth}{Boost free peer-reviewed portable C++ source libraries. \newline {\color{logoblue} \url{http://www.boost.org}}} \\ 
boost-gnu-openmpi-ohpc &
& \\ 
boost-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} boost-gnu7-mpich-ohpc &\multirow{3}{*}{1.67.0}
& \\ 
boost-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} boost-gnu8-mpich-ohpc &\multirow{2}{*}{1.69.0}
& \\ 
boost-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for boost

% <-- begin entry for fftw
fftw-gnu-mpich-ohpc &
\multirow{5}{*}{3.3.7} & 
\multirow{7}{\linewidth}{A Fast Fourier Transform library. \newline {\color{logoblue} \url{http://www.fftw.org}}} \\ 
fftw-gnu-openmpi-ohpc &
& \\ 
fftw-gnu7-mpich-ohpc &
& \\ 
fftw-gnu7-openmpi-ohpc &
& \\ 
fftw-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} fftw-gnu8-mpich-ohpc &\multirow{2}{*}{3.3.8}
& \\ 
fftw-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for fftw

% <-- begin entry for hypre
hypre-gnu-mpich-ohpc &
\multirow{3}{*}{2.13.0} & 
\multirow{7}{\linewidth}{Scalable algorithms for solving linear systems of equations. \newline {\color{logoblue} \url{http://www.llnl.gov/casc/hypre}}} \\ 
hypre-gnu-openmpi-ohpc &
& \\ 
hypre-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} hypre-gnu7-mpich-ohpc &\multirow{3}{*}{2.14.0}
& \\ 
hypre-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} hypre-gnu8-mpich-ohpc &\multirow{2}{*}{2.15.1}
& \\ 
hypre-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for hypre

% <-- begin entry for mfem
mfem-gnu7-mpich-ohpc &
\multirow{2}{*}{3.3.2} & 
\multirow{4}{\linewidth}{Lightweight, general, scalable C++ library for finite element methods. \newline {\color{logoblue} \url{http://mfem.org}}} \\ 
mfem-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} mfem-gnu8-mpich-ohpc &\multirow{2}{*}{3.4}
& \\ 
mfem-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for mfem

% <-- begin entry for mumps
mumps-gnu-mpich-ohpc &
\multirow{7}{*}{5.1.2} & 
\multirow{7}{\linewidth}{A MUltifrontal Massively Parallel Sparse direct Solver. \newline {\color{logoblue} \url{http://mumps.enseeiht.fr}}} \\ 
mumps-gnu-openmpi-ohpc &
& \\ 
mumps-gnu7-mpich-ohpc &
& \\ 
mumps-gnu7-openmpi-ohpc &
& \\ 
mumps-gnu7-openmpi3-ohpc &
& \\ 
mumps-gnu8-mpich-ohpc &
& \\ 
mumps-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for mumps

% <-- begin entry for opencoarrays
opencoarrays-gnu8-mpich-ohpc &
\multirow{2}{*}{2.2.0} & 
\multirow{2}{\linewidth}{ABI to leverage the parallel programming features of the Fortran 2018 DIS.  {\color{logoblue} \url{http://www.opencoarrays.org}}} \\ 
opencoarrays-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for opencoarrays

% <-- begin entry for petsc
petsc-gnu-mpich-ohpc &
\multirow{3}{*}{3.8.3} & 
\multirow{7}{\linewidth}{Portable Extensible Toolkit for Scientific Computation. \newline {\color{logoblue} \url{http://www.mcs.anl.gov/petsc}}} \\ 
petsc-gnu-openmpi-ohpc &
& \\ 
petsc-gnu7-openmpi-ohpc &
& \\ 
\cline{1-2} petsc-gnu7-mpich-ohpc &\multirow{3}{*}{3.9.1}
& \\ 
petsc-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} petsc-gnu8-mpich-ohpc &\multirow{2}{*}{3.10.3}
& \\ 
petsc-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for petsc

% <-- begin entry for ptscotch
ptscotch-gnu7-mpich-ohpc &
\multirow{3}{*}{6.0.4} & 
\multirow{5}{\linewidth}{Graph, mesh and hypergraph partitioning library using MPI. \newline {\color{logoblue} \url{http://www.labri.fr/perso/pelegrin/scotch}}} \\ 
ptscotch-gnu7-openmpi-ohpc &
& \\ 
ptscotch-gnu7-openmpi3-ohpc &
& \\ 
\cline{1-2} ptscotch-gnu8-mpich-ohpc &\multirow{2}{*}{6.0.6}
& \\ 
ptscotch-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for ptscotch

% <-- begin entry for scalapack
scalapack-gnu8-mpich-ohpc &
\multirow{2}{*}{2.0.2} & 
\multirow{2}{\linewidth}{A subset of LAPACK routines redesigned for heterogenous computing.  {\color{logoblue} \url{http://www.netlib.org/lapack-dev}}} \\ 
scalapack-gnu8-openmpi3-ohpc &
& \\ 
\hline
% <-- end entry for scalapack

% <-- begin entry for slepc
\bottomrule
\end{tabularx}
