\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for boost
boost-gnu-impi-fsp & 
\multirow{6}{*}{1.58.0} & 
\multirow{6}{\linewidth}{Boost free peer-reviewed portable C++ source libraries. \newline {\color{blue} http://www.boost.org}} \\ 
boost-gnu-mvapich2-fsp & 
& \\ 
boost-gnu-openmpi-fsp & 
& \\ 
boost-intel-impi-fsp & 
& \\ 
boost-intel-mvapich2-fsp & 
& \\ 
boost-intel-openmpi-fsp & 
& \\ 
\hline
% <-- end entry for boost

% <-- begin entry for fftw
fftw-gnu-impi-fsp & 
\multirow{3}{*}{3.3.4} & 
\multirow{3}{\linewidth}{A Fast Fourier Transform library. \newline {\color{blue} http://www.fftw.org}} \\ 
fftw-gnu-mvapich2-fsp & 
& \\ 
fftw-gnu-openmpi-fsp & 
& \\ 
\hline
% <-- end entry for fftw

% <-- begin entry for hypre
hypre-gnu-impi-fsp & 
\multirow{6}{*}{2.10.0b} & 
\multirow{6}{\linewidth}{Scalable algorithms for solving linear systems of equations. \newline {\color{blue} http://www.llnl.gov/casc/hypre}} \\ 
hypre-gnu-mvapich2-fsp & 
& \\ 
hypre-gnu-openmpi-fsp & 
& \\ 
hypre-intel-impi-fsp & 
& \\ 
hypre-intel-mvapich2-fsp & 
& \\ 
hypre-intel-openmpi-fsp & 
& \\ 
\hline
% <-- end entry for hypre

% <-- begin entry for mkl-blacs
mkl-blacs-gnu-openmpi-fsp & 
\multirow{1}{*}{11.3} & 
\multirow{1}{\linewidth}{Intel(R) Math Kernel Library Basic Linear Algebra Communication Subprograms.  {\color{blue} http://software.intel.com/en-us/intel-mkl}} \\ 
\hline
% <-- end entry for mkl-blacs

% <-- begin entry for mumps
mumps-gnu-impi-fsp & 
\multirow{6}{*}{5.0.0} & 
\multirow{6}{\linewidth}{A MUltifrontal Massively Parallel Sparse direct Solver. \newline {\color{blue} http://mumps.enseeiht.fr}} \\ 
mumps-gnu-mvapich2-fsp & 
& \\ 
mumps-gnu-openmpi-fsp & 
& \\ 
mumps-intel-impi-fsp & 
& \\ 
mumps-intel-mvapich2-fsp & 
& \\ 
mumps-intel-openmpi-fsp & 
& \\ 
\hline
% <-- end entry for mumps

% <-- begin entry for petsc
petsc-gnu-impi-fsp & 
\multirow{6}{*}{3.5.3} & 
\multirow{6}{\linewidth}{Portable Extensible Toolkit for Scientific Computation. \newline {\color{blue} http://www-unix.mcs.anl.gov/petsc/petsc-as}} \\ 
petsc-gnu-mvapich2-fsp & 
& \\ 
petsc-gnu-openmpi-fsp & 
& \\ 
petsc-intel-impi-fsp & 
& \\ 
petsc-intel-mvapich2-fsp & 
& \\ 
petsc-intel-openmpi-fsp & 
& \\ 
\hline
% <-- end entry for petsc

% <-- begin entry for superlu_dist
superlu\_dist-gnu-impi-fsp & 
\multirow{6}{*}{4.0} & 
\multirow{6}{\linewidth}{A general purpose library for the direct solution of linear equations. \newline {\color{blue} http://crd-legacy.lbl.gov/~xiaoye/SuperLU}} \\ 
superlu\_dist-gnu-mvapich2-fsp & 
& \\ 
superlu\_dist-gnu-openmpi-fsp & 
& \\ 
superlu\_dist-intel-impi-fsp & 
& \\ 
superlu\_dist-intel-mvapich2-fsp & 
& \\ 
superlu\_dist-intel-openmpi-fsp & 
& \\ 
\hline
% <-- end entry for superlu_dist

% <-- begin entry for trilinos
trilinos-gnu-impi-fsp & 
\multirow{6}{*}{11.14.3} & 
\multirow{6}{\linewidth}{A collection of libraries of numerical algorithms. \newline {\color{blue} http://trilinos.sandia.gov/index.html}} \\ 
trilinos-gnu-mvapich2-fsp & 
& \\ 
trilinos-gnu-openmpi-fsp & 
& \\ 
trilinos-intel-impi-fsp & 
& \\ 
trilinos-intel-mvapich2-fsp & 
& \\ 
trilinos-intel-openmpi-fsp & 
& \\ 
\hline
% <-- end entry for trilinos

\bottomrule
\end{tabularx}
