\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{r|X}
\toprule
{\bf Group Name} & {\bf Description} \\ 
\midrule

ohpc-adios & OpenHPC adios IO library builds for various compiler/MPI combinations. \\ 
ohpc-autotools & Collection of GNU autotools packages. \\ 
ohpc-base & OpenHPC base packages. \\ 
ohpc-boost & OpenHPC Boost library builds for various compiler/MPI combinations. \\ 
ohpc-fftw & OpenHPC FFTW library builds for various compiler/MPI combinations. \\ 
ohpc-gsl & OpenHPC GSL library builds for various compiler combinations. \\ 
ohpc-hdf5 & OpenHPC HDF5 library builds for various compiler combinations. \\ 
ohpc-hypre & OpenHPC Hypre library builds for various compiler/MPI combinations. \\ 
ohpc-imb & OpenHPC builds for Intel IMB MPI benchmarks. \\ 
ohpc-mpiP & OpenHPC mpiP profiling library builds for various compiler/MPI combinations. \\ 
ohpc-mumps & OpenHPC Mumps library builds for various compiler/MPI combinations. \\ 
ohpc-netcdf & OpenHPC NetCDF library builds for various compiler/MPI combinations. \\ 
ohpc-numpy & OpenHPC Numpy python module builds for various compiler combinations. \\ 
ohpc-petsc & OpenHPC PETSC library builds for various compiler/MPI combinations. \\ 
ohpc-scalapack & OpenHPC ScaLAPACK library builds for various compiler/MPI combinations. \\ 
ohpc-scipy & OpenHPC Scientific Python library builds for various compiler/MPI combinations. \\ 
ohpc-slurm-server & OpenHPC server packages for SLURM. \\ 
ohpc-tau & OpenHPC TAU library builds for various compiler/MPI combinations. \\ 
ohpc-trilinos & OpenHPC Trilinos library builds for various compiler/MPI combinations. \\ 
ohpc-warewulf & Collection of base packages for Warewulf provisioning. \\ 
ohpc-ganglia & Collection of Ganglia monitoring and metrics packages. \\ 
ohpc-metis & OpenHPC METIS library builds for various compiler combinations. \\ 
ohpc-nagios & Collection of Nagios monitoring and metrics packages. \\ 
ohpc-openblas & OpenHPC OpenBLAS library builds for various compiler combinations. \\ 
ohpc-phdf5 & OpenHPC HDF5 parallel library builds for various compiler/MPI combinations. \\ 
ohpc-slurm-client & OpenHPC client packages for SLURM. \\ 
ohpc-superlu\_dist & OpenHPC Superlu\_dist library builds for various compiler/MPI combinations. \\ 
\bottomrule
\end{tabularx}
