\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\ 
\midrule

% <-- begin entry for boost
boost-arm1-mpich-ohpc &
\multirow{2}{*}{1.73.0} & 
\multirow{4}{\linewidth}{Boost free peer-reviewed portable C++ source libraries. \newline {\color{logoblue} \url{http://www.boost.org}}} \\ 
boost-arm1-openmpi4-ohpc &
& \\ 
\cline{1-2} boost-gnu9-mpich-ohpc &\multirow{2}{*}{1.76.0}
& \\ 
boost-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for boost

% <-- begin entry for fftw
fftw-arm1-mpich-ohpc &
\multirow{4}{*}{3.3.8} & 
\multirow{4}{\linewidth}{A Fast Fourier Transform library. \newline {\color{logoblue} \url{http://www.fftw.org}}} \\ 
fftw-arm1-openmpi4-ohpc &
& \\ 
fftw-gnu9-mpich-ohpc &
& \\ 
fftw-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for fftw

% <-- begin entry for hypre
hypre-arm1-mpich-ohpc &
\multirow{4}{*}{2.18.1} & 
\multirow{4}{\linewidth}{Scalable algorithms for solving linear systems of equations. \newline {\color{logoblue} \url{http://www.llnl.gov/casc/hypre}}} \\ 
hypre-arm1-openmpi4-ohpc &
& \\ 
hypre-gnu9-mpich-ohpc &
& \\ 
hypre-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for hypre

% <-- begin entry for mfem
mfem-gnu9-mpich-ohpc &
\multirow{2}{*}{4.3} & 
\multirow{2}{\linewidth}{Lightweight, general, scalable C++ library for finite element methods.  {\color{logoblue} \url{http://mfem.org}}} \\ 
mfem-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for mfem

% <-- begin entry for mumps
mumps-arm1-mpich-ohpc &
\multirow{4}{*}{5.2.1} & 
\multirow{4}{\linewidth}{A MUltifrontal Massively Parallel Sparse direct Solver. \newline {\color{logoblue} \url{http://mumps.enseeiht.fr}}} \\ 
mumps-arm1-openmpi4-ohpc &
& \\ 
mumps-gnu9-mpich-ohpc &
& \\ 
mumps-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for mumps

% <-- begin entry for opencoarrays
opencoarrays-gnu9-mpich-ohpc &
\multirow{2}{*}{2.9.2} & 
\multirow{2}{\linewidth}{ABI to leverage the parallel programming features of the Fortran 2018 DIS.  {\color{logoblue} \url{http://www.opencoarrays.org}}} \\ 
opencoarrays-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for opencoarrays

% <-- begin entry for petsc
petsc-gnu9-mpich-ohpc &
\multirow{2}{*}{3.16.1} & 
\multirow{2}{\linewidth}{Portable Extensible Toolkit for Scientific Computation. \newline {\color{logoblue} \url{http://www.mcs.anl.gov/petsc}}} \\ 
petsc-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for petsc

% <-- begin entry for ptscotch
ptscotch-arm1-mpich-ohpc &
\multirow{4}{*}{6.0.6} & 
\multirow{4}{\linewidth}{Graph, mesh and hypergraph partitioning library using MPI. \newline {\color{logoblue} \url{http://www.labri.fr/perso/pelegrin/scotch}}} \\ 
ptscotch-arm1-openmpi4-ohpc &
& \\ 
ptscotch-gnu9-mpich-ohpc &
& \\ 
ptscotch-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for ptscotch

% <-- begin entry for scalapack
scalapack-arm1-mpich-ohpc &
\multirow{4}{*}{2.1.0} & 
\multirow{4}{\linewidth}{A subset of LAPACK routines redesigned for heterogenous computing. \newline {\color{logoblue} \url{http://www.netlib.org/lapack-dev}}} \\ 
scalapack-arm1-openmpi4-ohpc &
& \\ 
scalapack-gnu9-mpich-ohpc &
& \\ 
scalapack-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for scalapack

% <-- begin entry for slepc
slepc-gnu9-mpich-ohpc &
\multirow{2}{*}{3.16.0} & 
\multirow{2}{\linewidth}{A library for solving large scale sparse eigenvalue problems.  {\color{logoblue} \url{http://slepc.upv.es}}} \\ 
slepc-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for slepc

% <-- begin entry for superlu_dist
superlu\_dist-arm1-mpich-ohpc &
\multirow{2}{*}{6.1.1} & 
\multirow{4}{\linewidth}{A general purpose library for the direct solution of linear equations. \newline {\color{logoblue} \url{http://crd-legacy.lbl.gov/~xiaoye/SuperLU}}} \\ 
superlu\_dist-arm1-openmpi4-ohpc &
& \\ 
\cline{1-2} superlu\_dist-gnu9-mpich-ohpc &\multirow{2}{*}{6.4.0}
& \\ 
superlu\_dist-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for superlu_dist

% <-- begin entry for trilinos
trilinos-gnu9-mpich-ohpc &
\multirow{2}{*}{13.2.0} & 
\multirow{2}{\linewidth}{A collection of libraries of numerical algorithms. \newline {\color{logoblue} \url{https://trilinos.org}}} \\ 
trilinos-gnu9-openmpi4-ohpc &
& \\ 
\hline
% <-- end entry for trilinos

\bottomrule
\end{tabularx}
