\newcolumntype{C}[1]{>{\centering}p{#1}} 
\newcolumntype{L}[1]{>{\raggedleft}p{#1}} 
\small
\begin{tabularx}{\textwidth}{r|X}
\toprule
{\bf Group Name} & {\bf Description} \\ 
\midrule

ohpc-autotools & Collection of GNU autotools packages. \\ 
\hline
ohpc-base & Collection of base packages. \\ 
\hline
ohpc-base-compute & Collection of compute node base packages. \\ 
\hline
ohpc-ganglia & Collection of Ganglia monitoring and metrics packages. \\ 
\hline
ohpc-gnu8-geopm & Global Extensible Open Power Manager for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-io-libs & Collection of IO library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-mpich-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu8-mpich-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu8-mpich-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the MPICH runtime. \\ 
\hline
ohpc-gnu8-mvapich2-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the MVAPICH2 runtime. \\ 
\hline
ohpc-gnu8-mvapich2-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the MVAPICH2 runtime. \\ 
\hline
ohpc-gnu8-mvapich2-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the MVAPICH2 runtime. \\ 
\hline
ohpc-gnu8-openmpi3-io-libs & Collection of IO library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu8-openmpi3-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu8-openmpi3-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain and the OpenMPI runtime. \\ 
\hline
ohpc-gnu8-parallel-libs & Collection of parallel library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-perf-tools & Collection of performance tool builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-python-libs & Collection of python related library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-python2-libs & Collection of python2 related library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-python3-libs & Collection of python3 related library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-runtimes & Collection of runtimes for use with GNU compiler toolchain. \\ 
\hline
ohpc-gnu8-serial-libs & Collection of serial library builds for use with GNU compiler toolchain. \\ 
\hline
ohpc-intel-geopm & Global Extensible Open Power Manager for use with Intel(R) Parallel Studio XE software suite. \\ 
\hline
ohpc-intel-impi-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite and Intel(R) MPI runtime. \\ 
\hline
ohpc-intel-impi-parallel-libs & Collection of parallel library builds for use with Intel(R) Parallel Studio XE toolchain and the Intel(R) MPI Library. \\ 
\hline
ohpc-intel-impi-perf-tools & Collection of performance tool builds for use with Intel(R) Parallel Studio XE compiler toolchain and the Intel(R) MPI runtime. \\ 
\hline
ohpc-intel-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite. \\ 
\hline
ohpc-intel-mpich-io-libs & Collection of IO library builds for use with Intel(R) Parallel Studio XE software suite and MPICH runtime. \\ 
\hline
ohpc-intel-mpich-parallel-libs & Collection of parallel library builds for use with Intel(R) Parallel Studio XE toolchain and the MPICH runtime. \\ 
\hline
ohpc-intel-mpich-perf-tools & Collection of performance tool builds for use with Intel(R) Parallel Studio XE compiler toolchain and the MPICH runtime. \\ 
\hline
\bottomrule
\end{tabularx}
