% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}


\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


%%% % DOI
%%% \doi{10.475/123_4}

%%% % ISBN
%%% \isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{HPCSYSPROS '16}{November 14, 2016, Salt Lake City, UT, USA}

%%% \acmPrice{\$15.00}

%
% --- Author Metadata here ---
%%% \conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Cluster Computing with OpenHPC}
%%% \title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
%%% Format\titlenote{(Produces the permission block, and
%%% copyright information). For use with
%%% SIG-ALTERNATE.CLS. Supported by ACM.}}
%%% \subtitle{[Extended Abstract]
%%% \titlenote{A full version of this paper is available as
%%% \textit{Author's Guide to Preparing ACM SIG Proceedings Using
%%% \LaTeX$2_\epsilon$\ and BibTeX} at
%%% \texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
  %
% TODO: update all the authors at the end....
% 1st. author
%%%\alignauthor
%%%Karl Schulz\\
%%%       \affaddr{Intel Corp.}\\
%%%       \email{karl.w.schulz@intel.com}
%%%% 2nd. author
%%%\alignauthor
%%%Reese Baird\\
%%%       \affaddr{Intel Corp.}\\
%%%       \email{reese.baird@intel.com}
}

\maketitle
\begin{abstract}
OpenHPC is a Linux Foundation Collaborative Project whose mission is to provide
an integrated collection of HPC-centric software components that can be used to 
implement a full-featured reference HPC compute resource. Components span
the entire HPC software ecosystem including provisioning and system
administration tools, resource management, I/O services, development tools,
numerical libraries, and performance analysis tools.

Common clustering tools and scientific libraries are distributed as 
pre-built and validated binaries and are meant to seamlessly layer on top of 
existing Linux distributions. The architecture of OpenHPC is intentionally 
modular to allow end users to pick and choose from the provided components, as 
well as to foster a community of open contribution.

Packaging conventions, build and release infrastructure, and validation 
methodologies are described. We show how OpenHPC can be used to provision a 
fully usable scientific compute cluster.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010169</concept_id>
<concept_desc>Computing methodologies~Parallel computing
methodologies</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002944.10011122.10002947</concept_id>
<concept_desc>General and reference~General conference
proceedings</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940</concept_id>
<concept_desc>Software and its engineering~Software organization and properties</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Parallel computing methodologies}
\ccsdesc[300]{General and reference~General conference proceedings}
\ccsdesc[300]{Software and its engineering~Software organization and properties}


%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

%%% \keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}

\section{OpenHPC: Community building blocks for HPC systems}

\subsection{Motivation}
Many HPC sites spend considerable effort aggregating a large suite of 
open-source projects to provide a capable HPC environment for their users.
It is necessary to build and deploy HPC focused packages that are either absent
or outdated in Linux distro providers. Further, local packaging or 
customization frequently tries to give software versioning access to users (e.g.
via environment modules or similar equivalent). OpenHPC is focused on 
lowering the barrier to entry for HPC by providing a collection of 
pre-packaged and validated binary components that can be used to install 
and manage HPC clusters throughout their life cycle. We also provide multiple 
system configuration recipes that leverage community reference designs and best 
practices. 

\subsection{Governance \& Community}
Under the auspices of the Linux Foundation, OpenHPC has established a governing
board and a technical steering committee. The governing board is responsible for
budgetary oversight, intellectual property policies, marketing, and long-term
road map guidance. The technical steering committee is made up of representatives
from academia, industry, and government R\&D laboratories, and is tasked with
stack architecture, component selection, releases, and day-to-day project
maintenance.

\subsection{Conventions}
\subsubsection{Architecture}
We have assembled a variety of common ingredients required to deploy and manage 
an HPC Linux cluster including provisioning tools, resource management, I/O 
libraries, development tools, and a variety of scientific libraries. The 
delivery mechanism is via standard package managers (i.e., there are public 
OpenHPC repositories for both yum and zypper). OpenHPC currently supports CentOS
7 and SUSE's SLE 12. A single RPM spec file generates packages for both base
operating systems. This multiple target model also extends to compiler
toolchains and MPI runtime libraries. For some components that means a spec file
can generate 12 different versions of a package. This complexity is masked by
macros within the build system, and hierarchical Lmod environment modules are 
provided for users.

--example showing convenience group installation, package name convention, module
load--

\subsubsection{Build}

 - spec file conventions
 - git + OBS
 
\subsubsection{Test}
 To facilitate global efforts in diagnostics/validation, we have devised a standalone integration test infrastructure
 • Intent was to create families of tests that could be used during:
 - initial install process (can we build a system?)
 - post-install process (does it work?)
 - developing tests that touch all of the major components (can we compile against 3rd party libraries, will they execute under resource manager, etc)
 • Expectation is that each new component included will need corresponding integration test collateral
 • These integration tests are included in GitHub repo


\section{Conclusions \& Future work}
Some known big ticket items on the horizon for the TSC
- establishing a process and prioritization/selection process for including
new software components
- establish minimum integration test expectations
- establish packaging conventions:
• naming schemes
• dependency hierarchy management • installation paths
• upgrade/rollback? mechanisms
- road map time line for next release (and cadence strategy for future releases)
- addition of public CI infrastructure, roll out of additional architecture builds

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
\end{document}
